### 2021-07-04 paper/paper.tex
paper start

\documentclass{juliacon}

%\usepackage{xspace}
\setcounter{page}{1}

%\newcommand{\utd}{\texttt{UnitTestDesign}\xspace}
\newcommand{\utd}{UnitTestDesign}
\begin{document}

\input{header}

\maketitle

\begin{abstract}
The \utd package generates all-pairs test cases for unit tests. It implements a greedy algorithm that minimizes the number of test cases that give $n$-way combinatorial coverage. This library is meant to be convenient to use within Julia's unit testing framework, so you can specify forbidden combinations of arguments, to match the behavior of the function under test.
\end{abstract}

\section{Introduction}

We test code in order to address risk of failure, and we judge risk of failure by the likelihood code will fail, how difficult it is to mitigate a failure, and how important it is to have a correct result. However, whether the result of a calculation matters less than what's in the environment.

Our first unit tests for code often derive from mimicking how a user might write client code. These happy-path tests are narrative. We may augment them with our best guesses for corner cases of a function under test. There are times we want more of a guarantee that a function doesn't have faults. This may be that we recognize the function is complex, or that it's central to a sensitive calculation. We may test a part of a code base well because we want reduce the logical complexity that comes from doubt {cite}.

There is a world of testing tools to help find faults in risky code. Some measure the quality of existing tests. Others select tests to run depending on test coverage or recent code modifications. Let's focus on the first antidote to the biases inherent in narrative testing, those that generate test cases. These are tools that create argument values that you pass into a function under test. Then the author of the test is responsible for checking the validity of the output from the function.

There are a few common strategies for automated test case generation. A randomized approach chooses argument values from the space of allowed arguments, usually with some bias towards choosing possible corner cases. Some tools introduce more structure to choosing random arguments. The \texttt{QuickCheck} and \texttt{Hypothesis} packages use customized generators to create streams of test cases. Concolic testing records the execution of the function under test in order to generate subsequent test cases that are likely to increase line coverage. There are also more mathematical approachses, such as Sobol sequences and orthogonal arrays, which have particular diagnostic uses.

\section{Statement of Need}

Why we need n-way combinatorial testing. Why we need it in Julia.

Most of the techniques for test case generation focus more on making a smart set of tests then they focus on making few tests that are of high quality. Combinatorial testing generates fewer tests that are designed to give good branch coverage.

There are two cases where this is crucial. The first is that you have to test a slow function, such as a large, Monte Carlo inference. If the function under test runs for hours or days, then selective testing can respect resource limitations.

The other case is when there is a large test space. We've been talking about a function under test, but this is a stand-in for any test we can parametrize. Let's say we've written an application, that we've unit tested its important supporting functions, and we want to write user-level tests that look for problems from interactions among command-line arguments and choices in parameter files. This can be equivalent to testing a function with twenty or more arguments. Twenty arguments, with four possible values each, would lead to over $10^12$ ways to call this function, so how can we feel our tests begin to cover the problem?

The combinatorial testing in \utd takes the time to optimize the choice of test cases so that they can test the code well. The theory of the game is that each if--then in the code will branch depending on combinations of argument values, so combinatorial testing ensures all combinations of $n$ arguments are tried in at least one test case. Here, $n=2$ for two-way testing, also known as all-pairs testing, but studies have shown that wayness up to $n=6$ can be useful.

In practice, that means that you, the author of the unit test, has to choose a few possible values for each function argument. These values will be samples from equivalence classes for that argument and may include corner cases. Then the \utd library generates a set of test cases. In the unit testing framework, the code loops over the test cases, checking whether the results are acceptable.

While combinatorial testing is a useful tool in some circumstances, there are other tools that generate combinatorial tests. X makes them with a domain-specific language. This company's tool does it.

These companies keep disappearing. The quality of tools is supect (by the authors sometimes). It comes down to an author using the tools available within a framework.

That means the tool has to be usable, too. What happens if we create an all-pairs set of unit tests, but some of them don't work for your function because the combination of arguments doesn't make sense? You have to throw out those tests, but you've lost the very guarantee that this testing method made.
So it has to have a) forbid combinations of argument values, b) n-way testing c) multi-way testing d) start with certain cases.

\section{Solution}

So what we do here: Help anybody do a good job on this algorithm, thanks to some work we did.
Clarify the greedy algorithm. Show the algorithm with its complexity.
Out of scope: advanced data structures, other optimization methods.

An argument is. A value is.

The class of greedy algorithms:
The end result will be a list of test cases that have A columns, where A is the number of arguments.
\begin{enumerate}
   \item Generate a list of all combinations of argument values. For instance, one entry would be that the first value of the second argument must appear with the fourth value of the third argument.
   \item For an n-way coverage algorithm, initialize the first n columns of the test cases with a full factorial set of values.
   \item For each argument from n+1 to A.
   \begin{enumerate}
      \item Grow the test cases wider by finding all cases that match the next empty argument.
      \item Grow the test cases taller by adding a row for all cases that couldn't be matched.
   \end{enumerate}
   \item Fill in any missing values in test cases.
\end{enumerate}

\begin{lstlisting}[language=Julia]
function ipog(arity, n_way)
    nonincreasing = sortperm(arity, rev = true)
    arity = arity[nonincreasing]

    param_cnt = length(arity)
    # 2D array of argument values.
    test_set = all_combinations(
            arity[1:n_way], n_way)

    for param_idx in (n_way + 1):param_cnt
        taller = zeros(eltype(arity), param_idx,
                size(test_set, 2))
        taller[1:(param_idx - 1), :] .= test_set
        allc = one_parameter_combinations_matrix(
                arity[1:param_idx], n_way)
        choose_last_parameter!(taller, allc)
        test_set = insert_tuple_into_tests(
                taller, allc)
    end

    fill_remaining_missing_values!(test_set, arity)
    test_set[sortperm(nonincreasing), :]
end
\end{lstlisting}

If we pick one entry from the proposal and one entry from the test cases, there are five ways they can compare.
\begin{center}
\begin{tabular}{rll}
name & test cases & tuples \\ \hline
ignores & * & * \\
skips & $a$ & * \\
misses & * & $b$ \\
matches & $a$ & $b=a$ \\
mismatches & $a$ & $b\ne a$
\end{tabular}
\end{center}
Only the last comparison is clearly a mismatch.

Let's take two strings of argument values. Each pair of arguments will compare with one of the five ways. If any mismatch, there is a mismatch of the two strings. That leaves several different ways we can call a string matching. We can think of the string as scoring either zero or more than zero ignores, zero or more than zero skips, and so-on. That means there are $2^4-1 = 15$ ways for two strings to match, because nonzero strings will match at least one of the four ways. Which of the 15 ways do we count as a match?

\begin{enumerate}
   \item No mismatches.
   \item Some matches and no mismatches.
   \item Only matches, skips, or ignores. No misses or mismatches.
\end{enumerate}

1 and 2 are equivalent when the tuples all have a value in the current column being filled.
For filling the last tests, using no-mismatches works well.

\section{Comparison of Approaches}
to random
to generative

From a user perspective, it's about how easy it is to use one method or another. For instance, QuickCheck does more than generate tests. It reduces the cycle of debugging by finding the simplest test that fails.

to concolic

\section{Conclusion}
Residual logical complexity.

Unit test is a second telling of a function. A parable.

\input{bib.tex}
\end{document}

### 2021-07-05 paper/paper.tex
first edit

@@
+% JuliaCon proceedings template
 \documentclass{juliacon}
+\setcounter{page}{1}
+\usepackage{xspace}
+\newcommand{\utd}{\texttt{UnitTestDesign}\xspace}
 
-%\usepackage{xspace}
-\setcounter{page}{1}
-
-%\newcommand{\utd}{\texttt{UnitTestDesign}\xspace}
-\newcommand{\utd}{UnitTestDesign}
 \begin{document}
@@
 \begin{abstract}
+
 The \utd package generates all-pairs test cases for unit tests.
@@
 This library is meant to be convenient to use within Julia's unit testing framework, so you can specify forbidden combinations of arguments, to match the behavior of the function under test.
+
 \end{abstract}
@@
 We test code in order to address risk of failure, and we judge risk of failure by the likelihood code will fail, how difficult it is to mitigate a failure, and how important it is to have a correct result.
-However, whether the result of a calculation matters less than what's in the environment.
-
+However, whether the result of a calculation matters less than what's in the environment~\cite{Wiklund2017-ms}.
+\vskip 6pt
 Our first unit tests for code often derive from mimicking how a user might write client code.
@@
 This may be that we recognize the function is complex, or that it's central to a sensitive calculation.
-We may test a part of a code base well because we want reduce the logical complexity that comes from doubt {cite}.
+We may test a part of a code base well because we want reduce the logical complexity that comes from uncertainty~\cite{Sha2001-ie}.
 
+\vskip 6pt
 There is a world of testing tools to help find faults in risky code.
@@
 Let's focus on the first antidote to the biases inherent in narrative testing, those that generate test cases.
-These are tools that create argument values that you pass into a function under test.
-Then the author of the test is responsible for checking the validity of the output from the function.
 
+\vskip 6pt
+\begin{lstlisting}[language=Julia]
+using UnitTestDesign
+
+@enum Strategy naive keyfitz greville monotonic
+arg1 = [1, 4, 8]
+arg2 = [:a, :b, :c, :d]
+arg3 = [naive, keyfitz, greville, monotonic]
+arg4 = ["none", "RK4", "quadrature", "QUADPACK"]
+arg5 = [0.0, 9.3, -1.2, Inf]
+
+test_cases = all_pairs(arg1, arg2, arg3, arg4, arg5)
+for test_case in test_cases:
+    result = samplefunction(test_case...)
+    @assert known_invariant(result, test_case)
+end
+\end{lstlisting}
+
+Here, the \verb|all_pairs| function uses the sample argument values to create a set of test cases. The question is which set of cases it creates and when they are appropriate.
+
+\vskip 6pt
 There are a few common strategies for automated test case generation.
-A randomized approach chooses argument values from the space of allowed arguments, usually with some bias towards choosing possible corner cases.
+A randomized approach chooses argument values from the space of allowed arguments, usually with some bias towards choosing possible corner cases~\cite{Lampropoulos2020-sd,Arcuri2012-az}.
 Some tools introduce more structure to choosing random arguments.
-The \texttt{QuickCheck} and \texttt{Hypothesis} packages use customized generators to create streams of test cases.
-Concolic testing records the execution of the function under test in order to generate subsequent test cases that are likely to increase line coverage.
-There are also more mathematical approachses, such as Sobol sequences and orthogonal arrays, which have particular diagnostic uses.
+The \texttt{QuickCheck} and \texttt{Hypothesis} packages use customized generators to create streams of test cases~\cite{loscher2018automating}.
+Concolic testing records the execution of the function under test in order to generate subsequent test cases that are likely to increase line coverage~\cite{King1976-jt,Wang2018-xh}.
+There are also more mathematical approaches, such as Sobol sequences and orthogonal arrays~\cite{He2013-th}, which have particular diagnostic uses.
 
@@
 
-Most of the techniques for test case generation focus more on making a smart set of tests then they focus on making few tests that are of high quality.
-Combinatorial testing generates fewer tests that are designed to give good branch coverage.
+\vskip 6pt
+Most of the techniques for test case generation focus more on making a smart set of tests than they focus on making few tests that are of high quality.
+Combinatorial testing generates fewer tests that are designed to give good branch coverage~\cite{Nie2011-yl,Grindal2005-su,Kuhn2010-ak}.
 
+\vskip 6pt
 There are two cases where this is crucial.
@@
 
+\vskip 6pt
 The other case is when there is a large test space.
@@
 This can be equivalent to testing a function with twenty or more arguments.
-Twenty arguments, with four possible values each, would lead to over $10^12$ ways to call this function, so how can we feel our tests begin to cover the problem?
+Twenty arguments, with four possible values each, would lead to over $10^{12}$ ways to call this function, so how can we feel our tests begin to cover the problem?
 
+\vskip 6pt
 The combinatorial testing in \utd takes the time to optimize the choice of test cases so that they can test the code well.
@@
 
-In practice, that means that you, the author of the unit test, has to choose a few possible values for each function argument.
-These values will be samples from equivalence classes for that argument and may include corner cases.
-Then the \utd library generates a set of test cases.
-In the unit testing framework, the code loops over the test cases, checking whether the results are acceptable.
-
+\vskip 6pt
 While combinatorial testing is a useful tool in some circumstances, there are other tools that generate combinatorial tests. X makes them with a domain-specific language. This company's tool does it.
 
+\vskip 6pt
 These companies keep disappearing. The quality of tools is supect (by the authors sometimes). It comes down to an author using the tools available within a framework.
 
+\vskip 6pt
 That means the tool has to be usable, too.
@@
 You have to throw out those tests, but you've lost the very guarantee that this testing method made.
-So it has to have a) forbid combinations of argument values, b) n-way testing c) multi-way testing d) start with certain cases.
+So it has to have a) forbid combinations of argument values, b) n-way testing c) multi-way testing d) start with certain cases~\cite{Czerwonka2006-hm}.
 
-\section{Solution}
+\section{How to Use Combinatorial Testing}
 
+Depends on what your goals are.
+\begin{itemize}
+   \item At the top of the stack for comprehensive user-level testing.
+Here, you use the generator but then write test cases by creating command-line arguments and parameter files.
+Or you use it to create data sets with the given properties.
+   \item 
+   \end{itemize}
+Do the argument values represent:
+\begin{itemize}
+   \item Argument values for a function.
+   \item Equivalence classes from which to randomly choose values.
+   \item Directives on how to make a set of calls to an API.
+   \end{itemize}
+
+\vskip 6pt
+The person writing the unit tests has to pick the input values.
+In the same way that you would build up a decision table by selecting values from equivalence classes, you select values here.
+It can be an advantage in that you control the list and can make it more focused where you expect risk.
+It can be a disadvantage because your choice could exclude a value that random testing or concolic testing might discover exposes a fault.
+
+\vskip 6pt
+There are cases where a function has one argument that is a flag and, when it's chosen, other argument values don't make sense to choose.
+We want to forbid these from the possible input choices.
+For instance, if \verb|arg1| can be \verb|true| or \verb|false|, and \verb|arg2| can be \verb|default|, \verb|high|, or \verb|low|, but we want to exclude the combination of \verb|false| and \verb|high| or \verb|low|, then the possible outcomes are \verb|true|-\verb|default|, \verb|true|-\verb|high|, \verb|true|-\verb|low|, \verb|false|-\verb|default|.
+We can either teach the test generator to forbid two combinations, or we can modify the input values, so that \verb|arg12| represents the four possible cases for \verb|arg1| and \verb|arg2| together.
+
+Forbidden tuples~\cite{Petke2015-ex} for combinatorial testing is a method. Among others~\cite{Grindal2006-vy}.
+
+Mixed-level covering arrays don't have well-understood bounds~\cite{Cohen2003-pg}.
+
+\vskip 6pt
+Do the results represent exact values? For mathematical code, we often don't have exact values. You may check the results with
+\begin{itemize}
+   \item A different version of the same function, some kind of parallel implementation.
+Could be a more naive algorithm or one that uses a different mathematical representation of the same calculation.
+   \item A trait of the result, given the inputs.
+For instance, it may be that a second execution of the function under test, with the same arguments, modified to have \verb|f(2*a, b/2)=f(a, b)| should give the same result.
+This is a symmetry test~\cite{Segura2016-qh}.
+\end{itemize}
+
+\section{Optimization of Test Cases with Practical Constraints}
+Also \textsc{aetg}~\cite{Cohen1997-lb}.
+
+\vskip 6pt
 So what we do here: Help anybody do a good job on this algorithm, thanks to some work we did.
-Clarify the greedy algorithm. Show the algorithm with its complexity.
-Out of scope: advanced data structures, other optimization methods.
+Clarify the greedy algorithm~\cite{Lei2008-xt}. Show the algorithm with its complexity.
+Out of scope: advanced data structures~\cite{Segall2011-jv}, other optimization methods.
 
+\vskip 6pt
 An argument is. A value is.
 
+\vskip 6pt
 The class of greedy algorithms:
@@
 
+Higher arity for greedy algorithms is a relatively recent development~\cite{Richard_Kuhn2008-ut}.
+
+\vskip 6pt
 \begin{lstlisting}[language=Julia]
@@
 
+\vskip 6pt
 If we pick one entry from the proposal and one entry from the test cases, there are five ways they can compare.
@@
 
+\vskip 6pt
 Let's take two strings of argument values.
@@
 
+\vskip 6pt
 1 and 2 are equivalent when the tuples all have a value in the current column being filled.
@@
 \section{Comparison of Approaches}
+Classic criticism that coverage shouldn't be your goal~\cite{Inozemtseva2014-gz}. Counterpoint that coverage can be more meaningful for less-used paths in the code~\cite{Cai2005-ex}.
+
+\vskip 6pt
 to random
@@
 
+\vskip 6pt
 From a user perspective, it's about how easy it is to use one method or another.
@@
 
-to concolic
+\vskip 6pt
+to concolic~\cite{King1976-jt,Wang2018-xh}.
 
@@
 
+Combinatorial testing can benefit from simulated annealing~\cite{Petke2015-ex}.
+
+Another greedy algorithm~\cite{Calvagna2012-ic,Koc2018-vs}.
+
+This would work well with automated test selection if the the Julia testing framework defined tests such that they could be selected, as is done in X package.
+
+\vskip 6pt
 Unit test is a second telling of a function. A parable.
@@
 \input{bib.tex}
+
 \end{document}
+
+% Inspired by the International Journal of Computer Applications template

### 2021-07-05 paper/snippets.tex
first edit

\vskip 6pt
In practice, that means that you, the author of the unit test, has to choose a few possible values for each function argument. These values will be samples from equivalence classes for that argument and may include corner cases. Then the \utd library generates a set of test cases. In the unit testing framework, the code loops over the test cases, checking whether the results are acceptable.

### 2021-07-05 paper/paper.tex
decided structure for the user-friendly portion

@@
 The \texttt{QuickCheck} and \texttt{Hypothesis} packages use customized generators to create streams of test cases~\cite{loscher2018automating}.
-Concolic testing records the execution of the function under test in order to generate subsequent test cases that are likely to increase line coverage~\cite{King1976-jt,Wang2018-xh}.
+Concolic testing records the execution of the function under test in order to generate subsequent test cases that are likely to increase line coverage~\cite{King1976-jt,Wang2018-xh,vira2019}.
 There are also more mathematical approaches, such as Sobol sequences and orthogonal arrays~\cite{He2013-th}, which have particular diagnostic uses.
@@
 
-Why we need n-way combinatorial testing. Why we need it in Julia.
-
-\vskip 6pt
 Most of the techniques for test case generation focus more on making a smart set of tests than they focus on making few tests that are of high quality.
@@
 
-Depends on what your goals are.
-\begin{itemize}
-   \item At the top of the stack for comprehensive user-level testing.
-Here, you use the generator but then write test cases by creating command-line arguments and parameter files.
-Or you use it to create data sets with the given properties.
-   \item 
-   \end{itemize}
-Do the argument values represent:
-\begin{itemize}
-   \item Argument values for a function.
-   \item Equivalence classes from which to randomly choose values.
-   \item Directives on how to make a set of calls to an API.
-   \end{itemize}
+\subsection{Outline of the method}
+
+While you may already know how to use test case generation from the snippet in the introduction, it can help to think of automated test case generation as a set of steps, each of which has choices to make.
+\begin{enumerate}
+   \item Identify the system under test. It may be a function, but it could correspond to an \textsc{api} or an application.
+   \item Decide how a single test case, consisting of argument values, should correspond to a unit test.
+   \item Evaluate the risk associated with different arguments.
+   \item Pick a test generation strategy.
+   \item Choose a method for checking the results of each test.
+\end{enumerate}
+We'll explore these steps in this section.
+
+\subsection{Identify the system under test}
+
+We have assumed, thus far, that we are unit testing a function.
+In that case, the function has arguments and those arguments can take on particular values.
+Our test cases will correspond exactly to an invocation of the function.
+However, this need not be the case.
+The tool can be used more generally.
+Combinatorial testing is used outside Julia.
+It would apply, for instance, to testing compatibility of hardware subsystems.
+
+A common case in Julia is testing a scientific application at the user level.
+Here, we can consider the user's choices of command-line arguments and parameters in files.
+We could even generate classes of data according to keys that we assign to arguments in \utd.
+
+\subsection{Decide argument values}
+
+Some arguments to a function can take on only a few allowed values, such as \verb|true| or \verb|false|, but most arguments are integers, floating-point, or more complicated data structures.
+The theory of covering arrays presumes any argument will be assigned only one of a few values, so we need to make choices.
 
 \vskip 6pt
-The person writing the unit tests has to pick the input values.
-In the same way that you would build up a decision table by selecting values from equivalence classes, you select values here.
-It can be an advantage in that you control the list and can make it more focused where you expect risk.
-It can be a disadvantage because your choice could exclude a value that random testing or concolic testing might discover exposes a fault.
+We're looking for faults in the code that lead to failures of unit tests.
+These faults will be visible, or invisible, for different choices of argument values.
+If a given function fails for \verb|arg3<2.7|, then it will fail for \verb|arg3=2| as well as \verb|arg3=2.5|, so we consider those equivalent with respect to finding faults.
+Our goal, as authors of unit tests, is to select argument values that represent equivalence classes for the function under test.
+There isn't a lot of guidance on how to choose these values.
+You can guess them by looking at the code or by looking at a specification for the function.
+
+\vskip 6pt
+One way to defend against our uncertainty about equivalence classes is to combine combinatorial test generation with random testing.
+For each argument, partition the space of values into equivalence classes.
+Then generate test cases, but use the values in those test cases to select randomly from the partitions.
+This is one way to introduce bias, and control, into random test selection.
+It points to treating test case generation as a continuum of techniques.
+
+\vskip 6pt
+The argument values in test cases could also represent, for instance, the number of times to call a function on an \textsc{api}.
+The argument values could represent choices about what arguments to pass to each function in a series of function calls.
 
@@
 
+\subsection{Evaluate risk}
+
+The combinatorial testing approach gives you a lever with which to address perceived risk in code.
+This can range from pairwise testing, which is two-way coverage, to six-way coverage, beyond which studies show little benefit~\cite{Petke2015-ex}.
+corresponds to if--then.
+
+depends on resources.
+
+vary with sets of arguments.
 Mixed-level covering arrays don't have well-understood bounds~\cite{Cohen2003-pg}.
+
+Can after-the-fact measure differences in fault-finding.
+
+\subsection{Pick a test generation strategy}
+
+full factorial
+excursion
+n-way coverage
+ - by greedy
+ - by greedy, non-deterministic
+
+\subsection{Evaluate results}
+
+tend to use traits.
 
@@
 
+\vskip 6pt
+The person writing the unit tests has to pick the input values.
+In the same way that you would build up a decision table by selecting values from equivalence classes, you select values here.
+It can be an advantage in that you control the list and can make it more focused where you expect risk.
+It can be a disadvantage because your choice could exclude a value that random testing or concolic testing might discover exposes a fault.
+
 Another greedy algorithm~\cite{Calvagna2012-ic,Koc2018-vs}.

### 2021-07-05 paper/paper.tex
worked through most of the paper

@@
 \begin{abstract}
-
-The \utd package generates all-pairs test cases for unit tests.
-It implements a greedy algorithm that minimizes the number of test cases that give $n$-way combinatorial coverage.
-This library is meant to be convenient to use within Julia's unit testing framework, so you can specify forbidden combinations of arguments, to match the behavior of the function under test.
-
+Combinatorial interaction testing is an automated way to generate test cases for unit tests.
+It's designed to be the best guess at the fewest unit tests that will give the best coverage.
+This article discusses when to use this technique and how to apply it with the \utd package in the Julia testing ecosystem.
+This article offers a general approach to using automated test generation for different software testing applications.
 \end{abstract}
@@
 
-\section{Statement of Need}
+\section{Statement of Need}\label{sec:statement-of-need}
 
@@
 The theory of the game is that each if--then in the code will branch depending on combinations of argument values, so combinatorial testing ensures all combinations of $n$ arguments are tried in at least one test case.
-Here, $n=2$ for two-way testing, also known as all-pairs testing, but studies have shown that wayness up to $n=6$ can be useful.
+Here, $n=2$ for two-way testing, also known as all-pairs testing~\cite{pairwise-website}, but studies have shown that wayness up to $n=6$ can be useful~\cite{Petke2015-ex}.
 
@@
 
-\section{How to Use Combinatorial Testing}
+\section{How to Use Combinatorial Testing}\label{sec:how-to-use}
 
@@
    \item Decide how a single test case, consisting of argument values, should correspond to a unit test.
-   \item Evaluate the risk associated with different arguments.
+   \item Address the risk associated with different arguments.
    \item Pick a test generation strategy.
@@
 
+\vskip 6pt
 Forbidden tuples~\cite{Petke2015-ex} for combinatorial testing is a method. Among others~\cite{Grindal2006-vy}.
+\begin{lstlisting}[language=Julia]
+disallow(n, level, value, kind) = level == "high" && kind == :optim
+test_set = all_pairs(
+    [1, 2, 3], ["low", "mid" ,"high"], [1.0, 3.7, 4.9], [:greedy, :relax, :optim];
+    disallow = disallow
+    )
+\end{lstlisting}
 
-\subsection{Evaluate risk}
+\vskip 6pt
+Pre-existing example calls.
+\begin{lstlisting}[language=Julia]
+must_test = [[1, "mid", 3.7, :relax], [1, "mid", 4.9, :relax]]
+test_cases = all_pairs(
+    [1, 2, 3], ["low", "mid" ,"high"], [1.0, 3.7, 4.9], [:greedy, :relax, :optim];
+    seeds = must_test
+    )
+\end{lstlisting}
+
+\subsection{Address risk}
 
 The combinatorial testing approach gives you a lever with which to address perceived risk in code.
+You decide the wayness of coverage, which is the number of arguments for which all combinations of argument values must appear.
+Pairwise testing has two-way coverage.
+Literature on how to generate these tests uses the word coverage to mean two-way, three-way, and so on.
+The term test coverage usually refers to which lines of code, if--then decision tests, or branches are executed during a test.
+
+\vskip 6pt
+The two uses of the word coverage are related, because combinations with higher wayness should lead to more decision coverage of code.
+It would therefore seem appropriate to use cyclomatic complexity measures to estimate whether two-way coverage is enough.
+While there is some evidence that high coverage finds faults in less-used parts of a code base~\cite{Cai2005-ex}, coverage shouldn't be the focus of unit testing~\cite{Inozemtseva2014-gz}.
 This can range from pairwise testing, which is two-way coverage, to six-way coverage, beyond which studies show little benefit~\cite{Petke2015-ex}.
-corresponds to if--then.
 
-depends on resources.
+\vskip 6pt
+As described in Sec.~\ref{sec:statement-of-need}, combinatorial testing is most useful when there are constraints on testing resources.
+These constraints can force choices for the wayness of coverage.
+There are a couple of techniques for working within constraints, while still respecting our perception of risk.
 
-vary with sets of arguments.
-Mixed-level covering arrays don't have well-understood bounds~\cite{Cohen2003-pg}.
+\vskip 6pt
+The first is to vary wayness of coverage for different sets of arguments.
+For instance, if the function under test used an evolutionary algorithm that had several options for the representation of individuals, their mutation, and recombination, we might want to test these choices exhaustively with full-factorial coverage, while selecting pairwise coverage for other options.
+This would be done by adding a \verb|wayness| argument to the function call.
 
-Can after-the-fact measure differences in fault-finding.
+\begin{lstlisting}[language=Julia]
+array_of_forty_parameters = fill(1:4, 40)
+test_set = all_pairs(
+    array_of_forty_parameters...;
+    wayness = Dict(3 => [[3:6], [25:30]])
+    )
+\end{lstlisting}
+It's unclear whether mixing wayness will still yield a small set of test cases because mixed-level covering arrays don't have well-understood bounds~\cite{Cohen2003-pg}, however sample runs show it does produce fewer test cases than raising coverage on all arguments.
+
+\vskip 6pt
+One of the most powerful ways to address risk while conserving resources is to pair automated test generation with automated test selection.
+These are methods that evaluate the tests that are generated in order to select those that are most likely to find different faults in the code.
 
@@
 
-full factorial
-excursion
-n-way coverage
- - by greedy
- - by greedy, non-deterministic
+There are a few different strategies for combinatorial test generation in \utd.
+
+\vskip 6pt
+The \emph{full factorial} method generates $n$-way coverage for $n$ arguments.
+That is, it generates all combinations of values for all arguments.
+This is equivalent to what you could create with an $n$-deep for-loop.
+
+\vskip 6pt
+The \emph{excursion} method makes a first test case using the first provided value for each argument.
+Then, for one-way excursions, it walks the first argument through all values, keeping the rest of the arguments the same.
+Then it walks the second argument through all values, keeping the rest of the arguments the same.
+It asks how the function under test would perform if you were to change any single argument value.
+A two-way excursion tries changes to any two argument values in combination.
+
+\vskip 6pt
+There are two ways the \utd package creates covering arrays, also known as \emph{fractional factorial designs}.
+The default generator is called \verb|IPOG| because it is similar to the \textsc{ipo-g} algorithm~\cite{Lei2008-xt}.
+It is deterministic, so it produces the same set of test cases for the same set of inputs.
+The other generator is called \verb|GND|, and it uses a random number generator to search for covering arrays.
+It returns test cases that obey the same covering properties as the \verb|IPOG| generator, but it uses a method similar to the \textsc{aetg} generator~\cite{Cohen1997-lb}.
+In both cases, the algorithms vary from the published examples, as discussed in Sec.~\ref{sec:implementation}.
+
+\begin{lstlisting}[language=Julia]
+rng = Random.MersenneTwister(9790242)
+slow_and_short = all_pairs(parameters...; engine = GND(rng = rng, M = 50))
+\end{lstlisting}
 
@@
 
-tend to use traits.
+When a testing suite contains only a few tests of a function, the test author can usually figure out how to check those few function outputs for failures.
+Automatic generation of test arguments creates a problem because it isn't paired with automatic generation of checks for test failures.
 
 \vskip 6pt
-Do the results represent exact values? For mathematical code, we often don't have exact values. You may check the results with
-\begin{itemize}
-   \item A different version of the same function, some kind of parallel implementation.
-Could be a more naive algorithm or one that uses a different mathematical representation of the same calculation.
-   \item A trait of the result, given the inputs.
-For instance, it may be that a second execution of the function under test, with the same arguments, modified to have \verb|f(2*a, b/2)=f(a, b)| should give the same result.
-This is a symmetry test~\cite{Segura2016-qh}.
-\end{itemize}
-
-\section{Optimization of Test Cases with Practical Constraints}
-Also \textsc{aetg}~\cite{Cohen1997-lb}.
+One solution is to create a parallel implementation of the function under test.
+It could be an earlier version of the function, using a na{\"i}ve algorithm.
+It could be a function that computes the same values using a different mathematical representation, such as using numerical integration instead of using the result of symbolic integration.
+It could be an external implementation, in another language.
 
 \vskip 6pt
-So what we do here: Help anybody do a good job on this algorithm, thanks to some work we did.
-Clarify the greedy algorithm~\cite{Lei2008-xt}. Show the algorithm with its complexity.
-Out of scope: advanced data structures~\cite{Segall2011-jv}, other optimization methods.
+It helps to consider the check for failure, not as \verb|result == oracle(test_case...)| but as a rule that takes both result and test case into account.
+For instance, some mathematical calculations solve inverse problems, so that the result can be fed into a related forward problem.
+The test becomes whether it can recover its input values.
 
 \vskip 6pt
-An argument is. A value is.
+Automated testing of results often takes the form of testing for traits of the result, not exact values.
+For example, you could test a function for continuity of outputs near the given input.
+You could use statistical measures, such as maximum absolute error, to assert that a function's output is near some standard result.
+There is a powerful technique to assert symmetries in function arguments.
+For instance if, for some function under test, $f$, a symmetry test might check that \verb|f(a, b)=f(2*a, b/2)|~\cite{Segura2016-qh}.
+
+\section{Optimization of Test Cases with Practical Constraints}\label{sec:implementation}
+
+There are two ways to improve upon current use of combinatorial test generation.
+One is to help the tester whose testing resources are limited, by generating fewer test cases that still meet the wayness guarantee.
+The other is to make it more convenient to use combinatorial testing within the unit testing framework.
+Here, we could generate tests with so little time and memory that there is no need to cache test cases.
+Both of these improvements are limited by our need for algorithms that support the features, described above, that make automated test case generation practical to use.
 
 \vskip 6pt
-The class of greedy algorithms:
-The end result will be a list of test cases that have A columns, where A is the number of arguments.
-\begin{enumerate}
-   \item Generate a list of all combinations of argument values. For instance, one entry would be that the first value of the second argument must appear with the fourth value of the third argument.
-   \item For an n-way coverage algorithm, initialize the first n columns of the test cases with a full factorial set of values.
-   \item For each argument from n+1 to A.
-   \begin{enumerate}
-      \item Grow the test cases wider by finding all cases that match the next empty argument.
-      \item Grow the test cases taller by adding a row for all cases that couldn't be matched.
-   \end{enumerate}
-   \item Fill in any missing values in test cases.
-\end{enumerate}
-
-Higher arity for greedy algorithms is a relatively recent development~\cite{Richard_Kuhn2008-ut}.
+The \utd package expanded on the implementation of two $n$-way combinatorial interaction testing algorithms.
+One is the greedy, non-deterministic algorithm known as \textsc{aetg}~\cite{Cohen1997-lb}.
+The other is a deterministic, parameter-choosing algorithm called \textsc{ipo-g}~\cite{Lei2008-xt}.
+Like many greedy algorithms, these can be sensitive to small, sometimes unspecified, choices in implementation.
+We used two approaches for this package in order to make algorithms that had the right features and performed well.
 
 \vskip 6pt
-\begin{lstlisting}[language=Julia]
-function ipog(arity, n_way)
-    nonincreasing = sortperm(arity, rev = true)
-    arity = arity[nonincreasing]
-
-    param_cnt = length(arity)
-    # 2D array of argument values.
-    test_set = all_combinations(
-            arity[1:n_way], n_way)
-
-    for param_idx in (n_way + 1):param_cnt
-        taller = zeros(eltype(arity), param_idx,
-                size(test_set, 2))
-        taller[1:(param_idx - 1), :] .= test_set
-        allc = one_parameter_combinations_matrix(
-                arity[1:param_idx], n_way)
-        choose_last_parameter!(taller, allc)
-        test_set = insert_tuple_into_tests(
-                taller, allc)
-    end
-
-    fill_remaining_missing_values!(test_set, arity)
-    test_set[sortperm(nonincreasing), :]
-end
-\end{lstlisting}
+In order to support a feature where the test author can require certain pre-defined test cases, we added those test cases to the list of tuples to be covered, where a tuple is a combination of argument values.
+We just put that into the list and let the algorithms take care of covering it.
 
 \vskip 6pt
-If we pick one entry from the proposal and one entry from the test cases, there are five ways they can compare.
+In order to support multi-level wayness in coverage, we used multiple rounds of the official algorithm, starting at the highest wayness.
+For example, given a pairwise test generation strategy that requests all-triples over a set of five arguments, we first generated test cases that cover the all-triples, and then we presented these as initial seed values to the all-pairs calculation.
+
+\vskip 6pt
+In order to avoid forbidden combinations of arguments, we checked the validity of the next possible argument at every moment in the algorithm that a next argument is chosen.
+This sometimes meant that a test case being created could be thrown out and started new from a different seed argument value.
+This is a situation where it might help to use the Z3 theorem prover to reduce the need for retries, as some packages have done~\cite{Nie2011-yl}.
+
+\vskip 6pt
+There are a lot of choices in how to implement these algorithms, and they matter for speed and efficiency.
+The most important strategy for designing these algorithms was to generate an ensemble of algorithms and test them against sample inputs.
+
+\vskip 6pt
+For example, there is a common moment in these algorithms where a putative test case, partially specified, is matched against a coverage tuple, which will have $n$ specified argument values for $n$-way coverage.
+Given just one argument from the test case and one argument from the tuple, there are five ways they can compare.
 \begin{center}
 \begin{tabular}{rll}
-name & test cases & tuples \\ \hline
+comparison & test case & tuple \\ \hline
 ignores & * & * \\
@@
 Only the last comparison is clearly a mismatch.
+If we compare multiple arguments of the test case and tuple, we can quantify that comparison as having zero or more ``ignores,'' zero or more ``skips,'' and so-on.
+This means there are $2^4-1$ ways that a non-zero test case and tuple can compare, even if they have no mismatches.
 
 \vskip 6pt
-Let's take two strings of argument values.
-Each pair of arguments will compare with one of the five ways.
-If any mismatch, there is a mismatch of the two strings.
-That leaves several different ways we can call a string matching.
-We can think of the string as scoring either zero or more than zero ignores, zero or more than zero skips, and so-on.
-That means there are $2^4-1 = 15$ ways for two strings to match, because nonzero strings will match at least one of the four ways.
-Which of the 15 ways do we count as a match?
-
-\begin{enumerate}
-   \item No mismatches.
-   \item Some matches and no mismatches.
-   \item Only matches, skips, or ignores. No misses or mismatches.
-\end{enumerate}
+The \textsc{ipo-g} algorithm matches tuples in two places, once when it expands the number of columns of test cases and once when it fills in values at the end.
+In both cases, after testing $15\times 15$ ways of matching, we found that the simple requirement that there be no mismatches performed as well as any other choice, while more complicated matching strategies resulted in significantly more test cases for the same coverage.
 
 \vskip 6pt
-1 and 2 are equivalent when the tuples all have a value in the current column being filled.
-For filling the last tests, using no-mismatches works well.
+There are plenty of improvements to make to these algorithms, such as the use of advanced data structures~\cite{Segall2011-jv} or more adaptive optimization techniques like simulated annealing~\cite{Petke2015-ex}.
+There are also completely different greedy algorithms~\cite{Calvagna2012-ic,Koc2018-vs}.
+Any of these would be welcome to serve some use case if they can remain convenient to use within the testing framework.
 
-\section{Comparison of Approaches}
-Classic criticism that coverage shouldn't be your goal~\cite{Inozemtseva2014-gz}. Counterpoint that coverage can be more meaningful for less-used paths in the code~\cite{Cai2005-ex}.
+\section{Comparison of Approaches}\label{sec:comparison}
+
+Now that we've explored combinatorial interaction testing, let's return to place it in the context of other similar testing techniques.
+Compared to other methods for automated test case generation, combinatorial interaction testing makes fewer tests, with some wayness guarantees.
 
 \vskip 6pt
-to random
-to generative
+Random testing also generates test cases, and we know, from Arcuri et al, that these test cases increase code coverage with increasing numbers of test cases, in a predictable way~\cite{Arcuri2012-az}.
+Random testing also has the benefit that you can run it for an arbitrarily long time during acceptance testing.
+There is also no requirement that values be completely random within the domain of arguments.
+They are almost always biased towards values that carry risk, such as empty strings or other corner cases.
+Here, a preference for combinatorial interaction testing comes from a lack of test-running resources or the ease of specifying sample argument values instead of the complete domain of the arguments.
 
 \vskip 6pt
-From a user perspective, it's about how easy it is to use one method or another.
-For instance, QuickCheck does more than generate tests.
-It reduces the cycle of debugging by finding the simplest test that fails.
+There are also more mathematical test generation methods, such as orthogonal arrays or Sobol sequences~\cite{He2013-th}.
+These give an even distribution of values within high-dimensional spaces.
+They would be excellent to, for instance, seed an optimization problem with local minima, but they aren't designed to explore the space of execution paths of code, in the way that combinatorial methods are.
 
 \vskip 6pt
-to concolic~\cite{King1976-jt,Wang2018-xh}.
+There are also powerful testing methods that combine automated generation of test inputs with observation of test execution and outputs.
+For tests that run reasonably quickly, these strategies can shorten the time to find faults in the code, even if they don't shorten the length of a particular test run.
+
+\vskip 6pt
+Property-based testing offers domain-specific ways to describe the domain of each argument, or sets of arguments, so that the test author can focus on the domain of the function instead of the exact test suite.
+Tools of this kind can watch for failed tests, and then they can simplify the test arguments while checking for failure, in order to find the simplest test that fails.
+This is extraordinarily useful for fault-finding but, again, will use more testing resources~\cite{loscher2018automating}.
+
+\vskip 6pt
+Concolic testing performs the remarkable feat of executing a test case and recording that execution in order to learn which argument values control choices at each decision in the code.
+Then the concolic algorithm chooses a different argument value and tries the test again.
+This is an automated way to learn corner cases in the code, which should help with the challenge of deciding equivalence classes for arguments.
+At the same time, concolic testing generally uses logic solvers to decide equivalence classes, and these can be idiosyncratic for mathematical code~\cite{King1976-jt,Wang2018-xh}.
+The hardest part about concolic testing may be running it, conveniently, within the unit testing framework.
 
 \section{Conclusion}
+A lot of the strategies for using combinatorial testing, described in Sec.~\ref{sec:how-to-use}, also apply to competing methods for automated test case generation in Sec.~\ref{sec:comparison}.
+We showed that these methods apply to many kinds of software testing, from unit testing of functions to user-level testing of whole applications.
+We call them automated because the competing method is assiduous, manual creation of sets of unit tests.
+So automation is clearly an improvement.
+
+\vskip 6pt
+By showing how to use combinatorial interaction testing, we have shown that it should be used. This applies to other test generation techniques, too.
+
+\vskip 6pt
 Residual logical complexity.
 
-Combinatorial testing can benefit from simulated annealing~\cite{Petke2015-ex}.
-
 \vskip 6pt
-The person writing the unit tests has to pick the input values.
-In the same way that you would build up a decision table by selecting values from equivalence classes, you select values here.
-It can be an advantage in that you control the list and can make it more focused where you expect risk.
-It can be a disadvantage because your choice could exclude a value that random testing or concolic testing might discover exposes a fault.
-
-Another greedy algorithm~\cite{Calvagna2012-ic,Koc2018-vs}.
-
 This would work well with automated test selection if the the Julia testing framework defined tests such that they could be selected, as is done in X package.

### 2021-07-06 paper/paper.tex
edit after the park

@@
 \newcommand{\utd}{\texttt{UnitTestDesign}\xspace}
+\newcommand{\cit}{\textsc{cit}\xspace}
 
@@
 Combinatorial interaction testing is an automated way to generate test cases for unit tests.
-It's designed to be the best guess at the fewest unit tests that will give the best coverage.
+It's designed to be the best guess at the fewest unit tests that will give good decision coverage.
 This article discusses when to use this technique and how to apply it with the \utd package in the Julia testing ecosystem.
@@
 
-We test code in order to address risk of failure, and we judge risk of failure by the likelihood code will fail, how difficult it is to mitigate a failure, and how important it is to have a correct result.
-However, whether the result of a calculation matters less than what's in the environment~\cite{Wiklund2017-ms}.
-\vskip 6pt
-Our first unit tests for code often derive from mimicking how a user might write client code.
-These happy-path tests are narrative.
-We may augment them with our best guesses for corner cases of a function under test.
-There are times we want more of a guarantee that a function doesn't have faults.
-This may be that we recognize the function is complex, or that it's central to a sensitive calculation.
-We may test a part of a code base well because we want reduce the logical complexity that comes from uncertainty~\cite{Sha2001-ie}.
+We would like to think that our unit tests of code match perceived risk, that they match the components by which we judge risk: the hazard for failure, the cost of mitigating failure, and how much a result matters.
+However, user studies of the behavior of test authors show that much of our choices about testing are ruled by what is convenient within a given testing framework~\cite{Wiklund2017-ms}.
 
 \vskip 6pt
-There is a world of testing tools to help find faults in risky code.
+The first unit tests for a new library often derive from mimicking how a user might write client code.
+These happy-path tests are narrative.
+We may add tests that are our best guesses for corner cases of a function under test, but these are all considered manual testing.
+
+\vskip 6pt
+There is a world of automated testing tools.
 Some measure the quality of existing tests.
@@
 
-\vskip 6pt
 \begin{lstlisting}[language=Julia]
-using UnitTestDesign
+using UnitTestDesign: all_pairs
 
@@
 
-Here, the \verb|all_pairs| function uses the sample argument values to create a set of test cases. The question is which set of cases it creates and when they are appropriate.
+Here, the \verb|all_pairs| function is a combinatorial interaction test (\cit) design that uses the sample argument values to create a set of 16~test cases.
+It's a simple algorithm, with inputs that are easy to specify and use within an existing unit testing framework.
+The name, all-pairs, means that, if we look at the test cases, and we pick any two arguments, then pick any two values those arguments can take, there will be at least one test case that includes that pair of arguments.
+\begin{lstlisting}[language=Julia]
+julia> test_cases
+16-element Vector{Vector{Any}}:
+ [1, :a, naive, "none", 0.0]
+ [4, :a, keyfitz, "RK4", 9.3]
+ [8, :a, greville, "quadrature", -1.2]
+ [1, :a, monotonic, "QUADPACK", Inf]
+ [1, :b, naive, "RK4", -1.2]
+ [8, :b, keyfitz, "none", Inf]
+ [4, :b, greville, "QUADPACK", 0.0]
+ [1, :b, monotonic, "quadrature", 9.3]
+ [4, :c, naive, "quadrature", Inf]
+ [1, :c, keyfitz, "QUADPACK", -1.2]
+ [8, :c, greville, "none", 9.3]
+ [8, :c, monotonic, "RK4", 0.0]
+ [8, :d, naive, "QUADPACK", 9.3]
+ [1, :d, keyfitz, "quadrature", 0.0]
+ [1, :d, greville, "RK4", Inf]
+ [4, :d, monotonic, "none", -1.2]
+ \end{lstlisting}
+In this article, we describe when to use \cit and how to use \cit within the Julia language's unit testing ecosystem.
 
 \vskip 6pt
-There are a few common strategies for automated test case generation.
+\cit is one of a few common strategies for automated test case generation.
 A randomized approach chooses argument values from the space of allowed arguments, usually with some bias towards choosing possible corner cases~\cite{Lampropoulos2020-sd,Arcuri2012-az}.
@@
 Concolic testing records the execution of the function under test in order to generate subsequent test cases that are likely to increase line coverage~\cite{King1976-jt,Wang2018-xh,vira2019}.
-There are also more mathematical approaches, such as Sobol sequences and orthogonal arrays~\cite{He2013-th}, which have particular diagnostic uses.
+We will compare these methods in Sec.~\ref{sec:comparison}, after we understand the scope of combinatorial interaction testing.
 
@@
 
-Most of the techniques for test case generation focus more on making a smart set of tests than they focus on making few tests that are of high quality.
-Combinatorial testing generates fewer tests that are designed to give good branch coverage~\cite{Nie2011-yl,Grindal2005-su,Kuhn2010-ak}.
+Most of the techniques for automatic test case generation focus more on making a smart set of tests than they focus on making few tests that are of high quality.
+\cit generates fewer tests that are designed to give good branch coverage~\cite{Nie2011-yl,Grindal2005-su,Kuhn2010-ak}.
 
 \vskip 6pt
-There are two cases where this is crucial.
+There are two circumstances where this is crucial.
 The first is that you have to test a slow function, such as a large, Monte Carlo inference.
@@
 \vskip 6pt
-The other case is when there is a large test space.
+The other circumstance is when there is a large test space.
 We've been talking about a function under test, but this is a stand-in for any test we can parametrize.
@@
 This can be equivalent to testing a function with twenty or more arguments.
-Twenty arguments, with four possible values each, would lead to over $10^{12}$ ways to call this function, so how can we feel our tests begin to cover the problem?
+Twenty arguments, with four possible values each, would lead to over $10^{12}$ ways to call this function.
 
 \vskip 6pt
-The combinatorial testing in \utd takes the time to optimize the choice of test cases so that they can test the code well.
-The theory of the game is that each if--then in the code will branch depending on combinations of argument values, so combinatorial testing ensures all combinations of $n$ arguments are tried in at least one test case.
+The \cit in \utd takes the time to optimize the choice of test cases so that they can test the code well.
+The theory of the game is that each if--then in the code will branch depending on interacting combinations of argument values, so \cit ensures all combinations of $n$ arguments are tried in at least one test case.
 Here, $n=2$ for two-way testing, also known as all-pairs testing~\cite{pairwise-website}, but studies have shown that wayness up to $n=6$ can be useful~\cite{Petke2015-ex}.
@@
 \vskip 6pt
-While combinatorial testing is a useful tool in some circumstances, there are other tools that generate combinatorial tests. X makes them with a domain-specific language. This company's tool does it.
-
-\vskip 6pt
-These companies keep disappearing. The quality of tools is supect (by the authors sometimes). It comes down to an author using the tools available within a framework.
-
-\vskip 6pt
-That means the tool has to be usable, too.
-What happens if we create an all-pairs set of unit tests, but some of them don't work for your function because the combination of arguments doesn't make sense?
-You have to throw out those tests, but you've lost the very guarantee that this testing method made.
-So it has to have a) forbid combinations of argument values, b) n-way testing c) multi-way testing d) start with certain cases~\cite{Czerwonka2006-hm}.
+Lastly, even when \cit isn't the best of the automatic test case generation methods to use, it's easy specify tests and to insert them into a test suite, as we saw in the example above.
+There are excellent external \cit tools that define a domain-specific language for test specification and offer features that improve usability~\cite{Czerwonka2006-hm,Kuhn2010-ak}.
+The Julia environment offers both efficient integer computations necessary to generate test cases quickly and strong metaprogramming capabilities to make \cit simple to use.
 
@@
 \vskip 6pt
-In order to support multi-level wayness in coverage, we used multiple rounds of the official algorithm, starting at the highest wayness.
+In order to support multi-level wayness in coverage, we used multiple rounds of algorithms designed for single wayness, starting at the highest wayness.
 For example, given a pairwise test generation strategy that requests all-triples over a set of five arguments, we first generated test cases that cover the all-triples, and then we presented these as initial seed values to the all-pairs calculation.

### 2021-07-06 paper/snippets.tex
edit after the park

@@
 In the unit testing framework, the code loops over the test cases, checking whether the results are acceptable.
+
+ There are times we want more of a guarantee that a function doesn't have faults.
+This may be that we recognize the function is complex, or that it's central to a sensitive calculation.
+We may test a part of a code base well because we want reduce the logical complexity that comes from uncertainty~\cite{Sha2001-ie}.

### 2021-07-06 paper/paper.tex
through 3.3.1

@@
 \begin{enumerate}
-   \item Identify the system under test. It may be a function, but it could correspond to an \textsc{api} or an application.
+   \item Identify the system under test.
    \item Decide how a single test case, consisting of argument values, should correspond to a unit test.
@@
 However, this need not be the case.
-The tool can be used more generally.
-Combinatorial testing is used outside Julia.
-It would apply, for instance, to testing compatibility of hardware subsystems.
 
-A common case in Julia is testing a scientific application at the user level.
-Here, we can consider the user's choices of command-line arguments and parameters in files.
-We could even generate classes of data according to keys that we assign to arguments in \utd.
+\begin{unnumlist}
+\item Integration test of modules, where a module \textsc{api} produces many possible ways to call it.
+\item User-level tests of an application, where there are choices in dialog boxes, parameter files, and command-line options.
+\item Systems outside of Julia, such as the problem of hardware integration.
+\end{unnumlist}
 
@@
 
-Some arguments to a function can take on only a few allowed values, such as \verb|true| or \verb|false|, but most arguments are integers, floating-point, or more complicated data structures.
-The theory of covering arrays presumes any argument will be assigned only one of a few values, so we need to make choices.
+\subsubsection{What arguments represent}
+There are two choices to make about arguments and their values. We must decide what the arguments represent and must select particular values for those arguments.
 
 \vskip 6pt
-We're looking for faults in the code that lead to failures of unit tests.
-These faults will be visible, or invisible, for different choices of argument values.
-If a given function fails for \verb|arg3<2.7|, then it will fail for \verb|arg3=2| as well as \verb|arg3=2.5|, so we consider those equivalent with respect to finding faults.
+It's rare that a function expects arguments that really take only four possible values.
+We use integers, floating-point, and strings, but a function argument can be any struct.
+When we specify tests for \cit, and we choose a few argument values, they are representatives of equivalence classes.
+
+\vskip 6pt
+An \emph{equivalence class} is a set of input values that would discover the same faults in the code.
+For instance, if a given function fails for \verb|arg3<2.7|, then it will fail for \verb|arg3=2| as well as \verb|arg3=2.5|, so we consider those equivalent with respect to finding faults.
 Our goal, as authors of unit tests, is to select argument values that represent equivalence classes for the function under test.
@@
 One way to defend against our uncertainty about equivalence classes is to combine combinatorial test generation with random testing.
-For each argument, partition the space of values into equivalence classes.
-Then generate test cases, but use the values in those test cases to select randomly from the partitions.
+Decide that each argument value represents an equivalence class.
+Then generate test cases, but use the values in those test cases to sample randomly from the partitions.
 This is one way to introduce bias, and control, into random test selection.
@@
 \vskip 6pt
-The argument values in test cases could also represent, for instance, the number of times to call a function on an \textsc{api}.
-The argument values could represent choices about what arguments to pass to each function in a series of function calls.
+There are other creative ways to apply automatic test case generation.
+For instance, if an application reads a \textsc{csv} file, we can use \cit to ensure rows of that \textsc{csv} have a wide mixture of column values.
+This would improve branch coverage in code that reads the \textsc{csv} as a data frame.
+Similarly, for module-level testing, arguments could represent choices about calls to a module's functions.
+Here, consecutive arguments become function calls that are consecutive in time.
 
-\vskip 6pt
+\subsubsection{Controlling value choices}
+
 There are cases where a function has one argument that is a flag and, when it's chosen, other argument values don't make sense to choose.

### 2021-07-07 paper/paper.tex
a draft of the paper that's readable

@@
 \newcommand{\cit}{\textsc{cit}\xspace}
+\newcommand{\csv}{\textsc{csv}\xspace}
 
@@
 There are other creative ways to apply automatic test case generation.
-For instance, if an application reads a \textsc{csv} file, we can use \cit to ensure rows of that \textsc{csv} have a wide mixture of column values.
-This would improve branch coverage in code that reads the \textsc{csv} as a data frame.
+For instance, if an application reads a \csv file, we can use \cit to ensure rows of that \csv have a wide mixture of column values.
+This would improve branch coverage in code that reads the \csv as a data frame.
 Similarly, for module-level testing, arguments could represent choices about calls to a module's functions.
@@
 
-There are cases where a function has one argument that is a flag and, when it's chosen, other argument values don't make sense to choose.
-We want to forbid these from the possible input choices.
-For instance, if \verb|arg1| can be \verb|true| or \verb|false|, and \verb|arg2| can be \verb|default|, \verb|high|, or \verb|low|, but we want to exclude the combination of \verb|false| and \verb|high| or \verb|low|, then the possible outcomes are \verb|true|-\verb|default|, \verb|true|-\verb|high|, \verb|true|-\verb|low|, \verb|false|-\verb|default|.
-We can either teach the test generator to forbid two combinations, or we can modify the input values, so that \verb|arg12| represents the four possible cases for \verb|arg1| and \verb|arg2| together.
+Sometimes combinations of function arguments don't make sense. Imagine we have a function with two arguments.
+\begin{lstlisting}[language=Julia]
+arg1 = ["quick", "complicated"]
+arg2 = [0.0, 1.0, 10.0]
+\end{lstlisting}
+If the first argument is \verb|"quick"|, then the second argument must be \verb|0.0|.
+If we generate all combinations of \verb|arg1| and \verb|arg2|, then some combinations won't make sense.
+The domain of the function isn't merely the sum of the domains of the arguments.
+
+One way to solve this problem is to rewrite the argument list to have a single argument that reflects only the allowed combinations. This replaces \verb|arg1| and \verb|arg2|.
+\begin{lstlisting}[language=Julia]
+arg12 = [("quick", 0.0), ("complicated", 0.0),
+    ("complicated", 1.0), ("complicated", 10.0)]
+\end{lstlisting}
+It can be more convenient to tell the \cit algorithm that certain combinations are forbidden~\cite{Petke2015-ex,Grindal2006-vy}.
+\begin{lstlisting}[language=Julia]
+forbid(arg1, arg2) = arg1 == "quick" && arg2 > 0.0
+test_set = full_factorial(arg1, arg2, disallow = forbid)
+\end{lstlisting}
+For testing functions with many arguments, this is simpler to use.
 
 \vskip 6pt
-Forbidden tuples~\cite{Petke2015-ex} for combinatorial testing is a method. Among others~\cite{Grindal2006-vy}.
+Sometimes we want to begin with tests that are particular happy paths.
+These might be statistically common call signatures, or they could be pre-specified in design documents.
+Given that our goal is to minimize resource usage, we should ensure any tuples of argument values covered in these initial calls are included in our list of coverage.
 \begin{lstlisting}[language=Julia]
-disallow(n, level, value, kind) = level == "high" && kind == :optim
-test_set = all_pairs(
-    [1, 2, 3], ["low", "mid" ,"high"], [1.0, 3.7, 4.9], [:greedy, :relax, :optim];
-    disallow = disallow
-    )
-\end{lstlisting}
-
-\vskip 6pt
-Pre-existing example calls.
-\begin{lstlisting}[language=Julia]
-must_test = [[1, "mid", 3.7, :relax], [1, "mid", 4.9, :relax]]
+must_test = [[1, "mid", 3.7, :relax],
+             [1, "mid", 4.9, :relax]]
 test_cases = all_pairs(
-    [1, 2, 3], ["low", "mid" ,"high"], [1.0, 3.7, 4.9], [:greedy, :relax, :optim];
+    [1, 2, 3], ["low", "mid" ,"high"],
+    [1.0, 3.7, 4.9], [:greedy, :relax, :optim];
     seeds = must_test
@@
 \end{lstlisting}
+They are called seed cases and are easily specified.
 
@@
 You decide the wayness of coverage, which is the number of arguments for which all combinations of argument values must appear.
-Pairwise testing has two-way coverage.
+Pairwise testing has two-way coverage, but higher wayness can yield some benefit~\cite{Petke2015-ex}.
 Literature on how to generate these tests uses the word coverage to mean two-way, three-way, and so on.
-The term test coverage usually refers to which lines of code, if--then decision tests, or branches are executed during a test.
+The term test coverage usually refers to which lines of code executed (line coverage), if--then decision tests (decision coverage), or branches are executed during a test (branch coverage).
 
 \vskip 6pt
-The two uses of the word coverage are related, because combinations with higher wayness should lead to more decision coverage of code.
-It would therefore seem appropriate to use cyclomatic complexity measures to estimate whether two-way coverage is enough.
-While there is some evidence that high coverage finds faults in less-used parts of a code base~\cite{Cai2005-ex}, coverage shouldn't be the focus of unit testing~\cite{Inozemtseva2014-gz}.
-This can range from pairwise testing, which is two-way coverage, to six-way coverage, beyond which studies show little benefit~\cite{Petke2015-ex}.
+The two uses of the word coverage are related, because combinations with higher wayness as inputs are designed to lead to more decision coverage of code during execution.
+There isn't enough evidence for this connection for us to choose wayness according to code's cyclomatic complexity, and we are counseled against making coverage the goal of unit testing~\cite{Inozemtseva2014-gz}.
 
 \vskip 6pt
-As described in Sec.~\ref{sec:statement-of-need}, combinatorial testing is most useful when there are constraints on testing resources.
-These constraints can force choices for the wayness of coverage.
-There are a couple of techniques for working within constraints, while still respecting our perception of risk.
+For \cit, we address risk by ensuring more test cases include new combinations of arguments that affect the control flow of risky code.
+The first way to increase testing of an argument is to increase the number of values for an argument by adding corner cases.
+The second way is to increase the wayness of a set of arguments.
 
 \vskip 6pt
-The first is to vary wayness of coverage for different sets of arguments.
-For instance, if the function under test used an evolutionary algorithm that had several options for the representation of individuals, their mutation, and recombination, we might want to test these choices exhaustively with full-factorial coverage, while selecting pairwise coverage for other options.
+For example, if the function under test used an evolutionary algorithm that had several options for the representation of individuals, their mutation, and recombination, we might want to test these choices exhaustively with full-factorial coverage, while selecting pairwise coverage for other options.
 This would be done by adding a \verb|wayness| argument to the function call.
@@
 \end{lstlisting}
+Here, the third through sixth arguments will be tested with a wayness of three, as will the twenty-fifth through thirtieth.
 It's unclear whether mixing wayness will still yield a small set of test cases because mixed-level covering arrays don't have well-understood bounds~\cite{Cohen2003-pg}, however sample runs show it does produce fewer test cases than raising coverage on all arguments.
-
-\vskip 6pt
-One of the most powerful ways to address risk while conserving resources is to pair automated test generation with automated test selection.
-These are methods that evaluate the tests that are generated in order to select those that are most likely to find different faults in the code.
 
@@
 It asks how the function under test would perform if you were to change any single argument value.
-A two-way excursion tries changes to any two argument values in combination.
+A two-way excursion tries changes to any two argument values in combination, and so on.
 
@@
 
-\subsection{Evaluate results}
+\subsection{Evaluate results}\label{sec:results}
 
@@
 \section{Conclusion}
-A lot of the strategies for using combinatorial testing, described in Sec.~\ref{sec:how-to-use}, also apply to competing methods for automated test case generation in Sec.~\ref{sec:comparison}.
-We showed that these methods apply to many kinds of software testing, from unit testing of functions to user-level testing of whole applications.
-We call them automated because the competing method is assiduous, manual creation of sets of unit tests.
-So automation is clearly an improvement.
+Combinatorial interaction testing is an advanced technique because it's tailored to a difficult situation, when you can't afford not to spend the time to make your best guess at test cases.
+However, this kind of automation is easy to specify and run in Julia's ecosystem.
+The most difficult part of the transition is shifting from manual checks of test results to checks that work for any combination of arguments, as described in Sec.~\ref{sec:results}.
 
-\vskip 6pt
-By showing how to use combinatorial interaction testing, we have shown that it should be used. This applies to other test generation techniques, too.
-
-\vskip 6pt
-Residual logical complexity.
-
-\vskip 6pt
-This would work well with automated test selection if the the Julia testing framework defined tests such that they could be selected, as is done in X package.
-
-\vskip 6pt
-Unit test is a second telling of a function. A parable.
+A lot of the strategies in Sec.~\ref{sec:how-to-use} apply to any kind of automated test case generation.
+They point to the broad applicability of automation for testing and the effectiveness of tools that offer the test author control.
 

### 2021-07-08 paper/paper.tex
taking Joe's advice

@@
 Combinatorial interaction testing is an automated way to generate test cases for unit tests.
-It's designed to be the best guess at the fewest unit tests that will give good decision coverage.
-This article discusses when to use this technique and how to apply it with the \utd package in the Julia testing ecosystem.
-This article offers a general approach to using automated test generation for different software testing applications.
+It's designed to be a best guess at the fewest unit tests that will give good decision coverage.
+This article discusses when to use this technique, a general approach to using automated test generation for different software testing applications, and, in particular, how to apply it with the \utd package in the Julia testing ecosystem.
 \end{abstract}
@@
 These happy-path tests are narrative.
-We may add tests that are our best guesses for corner cases of a function under test, but these are all considered manual testing.
+We may add tests for corner cases of a function under test, but these may be limited by imagination and available effort.
 
@@
 
-Here, the \verb|all_pairs| function is a combinatorial interaction test (\cit) design that uses the sample argument values to create a set of 16~test cases.
-It's a simple algorithm, with inputs that are easy to specify and use within an existing unit testing framework.
+Here, the \verb|all_pairs| function is a combinatorial interaction test (\cit) design that uses the sample argument values to choose a set of 16~test cases out of a total possible 768~test cases.
+The inputs are easy to specify and use within an existing unit testing framework.
 The name, all-pairs, means that, if we look at the test cases, and we pick any two arguments, then pick any two values those arguments can take, there will be at least one test case that includes that pair of arguments.
@@
 
-Most of the techniques for automatic test case generation focus more on making a smart set of tests than they focus on making few tests that are of high quality.
-\cit generates fewer tests that are designed to give good branch coverage~\cite{Nie2011-yl,Grindal2005-su,Kuhn2010-ak}.
+Compared to other techniques for automatic test case generation, \cit generates fewer tests, choosing them in a way designed to give good branch coverage~\cite{Nie2011-yl,Grindal2005-su,Kuhn2010-ak}.
 
@@
 The \cit in \utd takes the time to optimize the choice of test cases so that they can test the code well.
-The theory of the game is that each if--then in the code will branch depending on interacting combinations of argument values, so \cit ensures all combinations of $n$ arguments are tried in at least one test case.
+The assumption is that each if--then in the code will branch depending on interacting combinations of argument values, so \cit ensures all combinations of $n$ arguments are tried in at least one test case.
 Here, $n=2$ for two-way testing, also known as all-pairs testing~\cite{pairwise-website}, but studies have shown that wayness up to $n=6$ can be useful~\cite{Petke2015-ex}.
@@
 
-\begin{unnumlist}
+\begin{itemize}
 \item Integration test of modules, where a module \textsc{api} produces many possible ways to call it.
@@
 \item Systems outside of Julia, such as the problem of hardware integration.
-\end{unnumlist}
+\end{itemize}
 
@@
 For instance, if a given function fails for \verb|arg3<2.7|, then it will fail for \verb|arg3=2| as well as \verb|arg3=2.5|, so we consider those equivalent with respect to finding faults.
-Our goal, as authors of unit tests, is to select argument values that represent equivalence classes for the function under test.
-There isn't a lot of guidance on how to choose these values.
-You can guess them by looking at the code or by looking at a specification for the function.
+As authors of unit tests, we select argument values that represent equivalence classes for the function under test.
+You can choose them by looking at the code or by looking at a specification for the function, but it's possible to miss an equivalence class and miss the faults discovered by that equivalence class.
 
@@
 One way to defend against our uncertainty about equivalence classes is to combine combinatorial test generation with random testing.
-Decide that each argument value represents an equivalence class.
-Then generate test cases, but use the values in those test cases to sample randomly from the partitions.
-This is one way to introduce bias, and control, into random test selection.
+Decide that each argument value in the \cit specification represents a generator of values from an equivalence class.
+Then each test case, output from \cit, is a list of random argument generators.
+This introduces bias, and control, into random test selection.
 It points to treating test case generation as a continuum of techniques.
@@
 \begin{lstlisting}[language=Julia]
-rng = Random.MersenneTwister(9790242)
+rng = Random.MersenneTwister(9790375)
 slow_and_short = all_pairs(parameters...; engine = GND(rng = rng, M = 50))
@@
 \vskip 6pt
-It helps to consider the check for failure, not as \verb|result == oracle(test_case...)| but as a rule that takes both result and test case into account.
+It helps to consider the check for failure, not as an assertion about the result,
+\begin{lstlisting}[language=Julia]
+@assert result == oracle(test_case...)
+\end{lstlisting}
+but as a rule that takes both result and test case into account.
+\begin{lstlisting}[language=Julia]
+@assert invariant(result, test_case...)
+\end{lstlisting}
 For instance, some mathematical calculations solve inverse problems, so that the result can be fed into a related forward problem.
 The test becomes whether it can recover its input values.
-
-\vskip 6pt
-Automated testing of results often takes the form of testing for traits of the result, not exact values.
-For example, you could test a function for continuity of outputs near the given input.
-You could use statistical measures, such as maximum absolute error, to assert that a function's output is near some standard result.
-There is a powerful technique to assert symmetries in function arguments.
-For instance if, for some function under test, $f$, a symmetry test might check that \verb|f(a, b)=f(2*a, b/2)|~\cite{Segura2016-qh}.
+Another test would be whether nearby inputs give continuous outputs.
+Lastly, a technique to assert symmetries in function arguments, when such symmetries exist in the function under test, has been shown to find faults~\cite{Segura2016-qh}.
+For instance, for some function under test, $f$, a symmetry test might check that \verb|f(a, b)=f(2*a, b/2)|.
 
@@
 \vskip 6pt
-The \utd package expanded on the implementation of two $n$-way combinatorial interaction testing algorithms.
+The \utd package expands on the implementation of two $n$-way combinatorial interaction testing algorithms.
 One is the greedy, non-deterministic algorithm known as \textsc{aetg}~\cite{Cohen1997-lb}.
@@
 This means there are $2^4-1$ ways that a non-zero test case and tuple can compare, even if they have no mismatches.
-
-\vskip 6pt
-The \textsc{ipo-g} algorithm matches tuples in two places, once when it expands the number of columns of test cases and once when it fills in values at the end.
-In both cases, after testing $15\times 15$ ways of matching, we found that the simple requirement that there be no mismatches performed as well as any other choice, while more complicated matching strategies resulted in significantly more test cases for the same coverage.
+The \utd library has tuned its search for test cases by optimizing across these matching algorithms.
 
@@
 \vskip 6pt
-Property-based testing offers domain-specific ways to describe the domain of each argument, or sets of arguments, so that the test author can focus on the domain of the function instead of the exact test suite.
+Property-based testing offers a specification to describe the domain of each argument, or sets of arguments, so that the test author can focus on the domain of the function instead of the exact test suite.
 Tools of this kind can watch for failed tests, and then they can simplify the test arguments while checking for failure, in order to find the simplest test that fails.

### 2021-07-09 paper/paper.tex
added a table of numbers and amended statement of need last para

@@
 It's designed to be a best guess at the fewest unit tests that will give good decision coverage.
-This article discusses when to use this technique, a general approach to using automated test generation for different software testing applications, and, in particular, how to apply it with the \utd package in the Julia testing ecosystem.
+This article discusses when to use this technique, offers a general approach to using automated test generation for different software testing applications, and shows how to apply it with the \utd package in the Julia testing ecosystem.
 \end{abstract}
@@
 We would like to think that our unit tests of code match perceived risk, that they match the components by which we judge risk: the hazard for failure, the cost of mitigating failure, and how much a result matters.
-However, user studies of the behavior of test authors show that much of our choices about testing are ruled by what is convenient within a given testing framework~\cite{Wiklund2017-ms}.
+However, user studies of the behavior of test authors show that our choices about testing are ruled by what is convenient within a given testing framework~\cite{Wiklund2017-ms}.
 
@@
 These happy-path tests are narrative.
-We may add tests for corner cases of a function under test, but these may be limited by imagination and available effort.
+We may add tests for corner cases of a function under test, but these are limited by imagination and available effort.
 
 \vskip 6pt
-There is a world of automated testing tools.
+Automated testing tools aid that effort.
 Some measure the quality of existing tests.
-Others select tests to run depending on test coverage or recent code modifications.
-Let's focus on the first antidote to the biases inherent in narrative testing, those that generate test cases.
+Others select which tests to run depending on test coverage or recent code modifications.
+Let's focus on the first antidote to the biases inherent in narrative testing, automated generation of test cases.
 
@@
 Here, the \verb|all_pairs| function is a combinatorial interaction test (\cit) design that uses the sample argument values to choose a set of 16~test cases out of a total possible 768~test cases.
-The inputs are easy to specify and use within an existing unit testing framework.
+The inputs are specified as explicit lists of argument values.
 The name, all-pairs, means that, if we look at the test cases, and we pick any two arguments, then pick any two values those arguments can take, there will be at least one test case that includes that pair of arguments.
@@
 \end{lstlisting}
+For a three-way \cit, we could pick any three arguments and any three values those arguments can take, and there will be at least one test case including that triple.
 In this article, we describe when to use \cit and how to use \cit within the Julia language's unit testing ecosystem.
@@
 \cit is one of a few common strategies for automated test case generation.
-A randomized approach chooses argument values from the space of allowed arguments, usually with some bias towards choosing possible corner cases~\cite{Lampropoulos2020-sd,Arcuri2012-az}.
+A randomized strategy chooses argument values from the space of allowed arguments, usually with some bias towards choosing possible corner cases~\cite{Lampropoulos2020-sd,Arcuri2012-az}.
 Some tools introduce more structure to choosing random arguments.
@@
 
-Compared to other techniques for automatic test case generation, \cit generates fewer tests, choosing them in a way designed to give good branch coverage~\cite{Nie2011-yl,Grindal2005-su,Kuhn2010-ak}.
+Compared to other techniques for automatic test case generation, \cit generates fewer tests, choosing them in a way designed to give good decision coverage~\cite{Nie2011-yl,Grindal2005-su,Kuhn2010-ak}.
 
@@
 The \cit in \utd takes the time to optimize the choice of test cases so that they can test the code well.
-The assumption is that each if--then in the code will branch depending on interacting combinations of argument values, so \cit ensures all combinations of $n$ arguments are tried in at least one test case.
-Here, $n=2$ for two-way testing, also known as all-pairs testing~\cite{pairwise-website}, but studies have shown that wayness up to $n=6$ can be useful~\cite{Petke2015-ex}.
+The assumption is that each if--then in the code will branch depending on interacting combinations of argument values, so \cit ensures all combinations of $t$ arguments are tried in at least one test case.
+Here, $t=2$ for two-way testing, also known as all-pairs testing~\cite{pairwise-website}, but studies have shown that wayness up to $t=6$ can be useful~\cite{Petke2015-ex}.
 
 \vskip 6pt
-Lastly, even when \cit isn't the best of the automatic test case generation methods to use, it's easy specify tests and to insert them into a test suite, as we saw in the example above.
-There are excellent external \cit tools that define a domain-specific language for test specification and offer features that improve usability~\cite{Czerwonka2006-hm,Kuhn2010-ak}.
-The Julia environment offers both efficient integer computations necessary to generate test cases quickly and strong metaprogramming capabilities to make \cit simple to use.
+Lastly, there are excellent external \cit tools that define a domain-specific language for test specification and offer features that improve usability~\cite{Czerwonka2006-hm,Kuhn2010-ak}.
+However, having \cit within the Julia environment not only makes it easier to import as a library, but also takes advantage of Julia's strengths as a language.
+The simple interface for arguments and forbidden combinations (covered below) depends on dynamic typing.
+The speed of the underlying algorithms depends on Julia's ability to create efficient numerical code.
 
@@
 
-While you may already know how to use test case generation from the snippet in the introduction, it can help to think of automated test case generation as a set of steps, each of which has choices to make.
+While you may already know how to use \cit from the snippet in the introduction, it can help to think of automated test case generation as a set of steps, each of which has choices to make.
 \begin{enumerate}
@@
 However, this need not be the case.
+The same idea of interacting choices applies to other test targets:
 
@@
 \vskip 6pt
-It's rare that a function expects arguments that really take only four possible values.
+It's rare that a function expects arguments that really take only a few possible values.
 We use integers, floating-point, and strings, but a function argument can be any struct.
@@
 Decide that each argument value in the \cit specification represents a generator of values from an equivalence class.
-Then each test case, output from \cit, is a list of random argument generators.
+Then each test case, output from \cit, is a list of generators of random arguments.
 This introduces bias, and control, into random test selection.
@@
 
-\subsubsection{Controlling value choices}
+\subsubsection{Control value choices}
 
@@
 \end{lstlisting}
-If the first argument is \verb|"quick"|, then the second argument must be \verb|0.0|.
+For this example, if the first argument is \verb|"quick"|, then the second argument must be \verb|0.0|.
 If we generate all combinations of \verb|arg1| and \verb|arg2|, then some combinations won't make sense.
@@
 
+\vskip 6pt
 One way to solve this problem is to rewrite the argument list to have a single argument that reflects only the allowed combinations. This replaces \verb|arg1| and \verb|arg2|.
@@
 forbid(arg1, arg2) = arg1 == "quick" && arg2 > 0.0
-test_set = full_factorial(arg1, arg2, disallow = forbid)
+test_set = full_factorial(
+    arg1, arg2; disallow = forbid)
 \end{lstlisting}
@@
 These might be statistically common call signatures, or they could be pre-specified in design documents.
-Given that our goal is to minimize resource usage, we should ensure any tuples of argument values covered in these initial calls are included in our list of coverage.
+Given that our goal is to minimize resource usage, we should ensure that any tuples of argument values covered in these initial calls are included in our list of covered tuples.
 \begin{lstlisting}[language=Julia]
@@
 \end{lstlisting}
-They are called seed cases and are easily specified.
+They are called seed cases and are specified with an explicit option in \utd.
 
@@
 You decide the wayness of coverage, which is the number of arguments for which all combinations of argument values must appear.
+As shown in Tab.~\ref{tab:samplecounts}, increasing wayness increases the number of test cases.
 Pairwise testing has two-way coverage, but higher wayness can yield some benefit~\cite{Petke2015-ex}.
 Literature on how to generate these tests uses the word coverage to mean two-way, three-way, and so on.
-The term test coverage usually refers to which lines of code executed (line coverage), if--then decision tests (decision coverage), or branches are executed during a test (branch coverage).
+The term test coverage usually refers to which lines of code executed (line coverage), if--then decision tests (decision coverage), or branches that are executed during a test (branch coverage).
 
@@
 \vskip 6pt
-The \emph{full factorial} method generates $n$-way coverage for $n$ arguments.
+The \emph{full factorial} method generates $t$-way coverage for $t$ arguments.
 That is, it generates all combinations of values for all arguments.
-This is equivalent to what you could create with an $n$-deep for-loop.
+This is equivalent to what you could create with an $t$-deep for-loop.
 
@@
 Then, for one-way excursions, it walks the first argument through all values, keeping the rest of the arguments the same.
-Then it walks the second argument through all values, keeping the rest of the arguments the same.
+Then it walks the second argument through all values, keeping the rest of the arguments the same, and so on.
 It asks how the function under test would perform if you were to change any single argument value.
-A two-way excursion tries changes to any two argument values in combination, and so on.
+A two-way excursion tries changes to any two argument values in combination.
+It produces considerably more test cases than an all-pairs design.
+
+\begin{table}
+\tbl{Count of test cases from different test generation strategies.\label{tab:samplecounts}}{
+\begin{tabular}{ll|lllll}
+ & & Total & \multicolumn{2}{c}{$t$-way} & \multicolumn{2}{c}{Excursions} \\
+Args & Vals & Combinations & Pairs & Triples & Single & Pair \\ \hline
+5 & 4 & 1024 & 16 & 64 & 16 & 106 \\ \hline
+5 & 8 & 32768 & 96 & 768 & 36 & 526 \\ \hline
+10 & 4 & $>10^{6}$ & 28 & 143 & 31 & 436 \\ \hline
+10 & 8 & $>10^{9}$ & 113 & 1223 & 71 & 2276 \\ \hline
+40 & 4 & $>10^{24}$ & 45 & 290 & 121 & 7141 \\ \hline
+40 & 8 & $>10^{36}$ & 166 & 2388 & 281 & 38501 \\  \hline
+\end{tabular}
+}
+\end{table}
 
@@
 In both cases, the algorithms vary from the published examples, as discussed in Sec.~\ref{sec:implementation}.
-
 \begin{lstlisting}[language=Julia]
 rng = Random.MersenneTwister(9790375)
-slow_and_short = all_pairs(parameters...; engine = GND(rng = rng, M = 50))
+slow_and_short = all_triples(parameters...; engine = GND(rng = rng, M = 50))
 \end{lstlisting}
+The \verb|M=50| argument to the \verb|GND| generator controls the number of times it guesses each new argument of a test case before chooses an optimal value.
 
@@
 Here, we could generate tests with so little time and memory that there is no need to cache test cases.
-Both of these improvements are limited by our need for algorithms that support the features, described above, that make automated test case generation practical to use.
+Both of these improvements are limited by our need for algorithms that support the features, described in Sec.~\ref{sec:how-to-use}, that make automated test case generation practical to use.
 
 \vskip 6pt
-The \utd package expands on the implementation of two $n$-way combinatorial interaction testing algorithms.
+The \utd package expands on the implementation of two $t$-way combinatorial interaction testing algorithms.
 One is the greedy, non-deterministic algorithm known as \textsc{aetg}~\cite{Cohen1997-lb}.
 The other is a deterministic, parameter-choosing algorithm called \textsc{ipo-g}~\cite{Lei2008-xt}.
-Like many greedy algorithms, these can be sensitive to small, sometimes unspecified, choices in implementation.
-We used two approaches for this package in order to make algorithms that had the right features and performed well.
+Thile these algorithms have different structure, we were able to add features to them using similar basic moves.
 
 \vskip 6pt
-In order to support a feature where the test author can require certain pre-defined test cases, we added those test cases to the list of tuples to be covered, where a tuple is a combination of argument values.
+In order to support a feature where the test author can require certain pre-defined test cases, we add those test cases to the list of tuples to be covered, where a tuple is a combination of argument values.
 We just put that into the list and let the algorithms take care of covering it.
@@
 \vskip 6pt
-In order to support multi-level wayness in coverage, we used multiple rounds of algorithms designed for single wayness, starting at the highest wayness.
-For example, given a pairwise test generation strategy that requests all-triples over a set of five arguments, we first generated test cases that cover the all-triples, and then we presented these as initial seed values to the all-pairs calculation.
+In order to support multi-level wayness in coverage, we use multiple rounds of algorithms designed for single wayness, starting at the highest wayness.
+For example, given a pairwise test generation strategy that requests all-triples over a set of five arguments, we first generate test cases that cover the all-triples and then present these as initial seed values to the all-pairs calculation.
 
 \vskip 6pt
-In order to avoid forbidden combinations of arguments, we checked the validity of the next possible argument at every moment in the algorithm that a next argument is chosen.
-This sometimes meant that a test case being created could be thrown out and started new from a different seed argument value.
-This is a situation where it might help to use the Z3 theorem prover to reduce the need for retries, as some packages have done~\cite{Nie2011-yl}.
+In order to avoid forbidden combinations of arguments, we check the validity of the next possible argument at every moment in the algorithm that a next argument is chosen.
+This sometimes means that a test case being created could be thrown out and started new from a different seed argument value.
+This is a situation where it might help to use the \textsc{z3} theorem prover to reduce the need for retries, as some packages have done~\cite{Nie2011-yl}.
 
 \vskip 6pt
-There are a lot of choices in how to implement these algorithms, and they matter for speed and efficiency.
-The most important strategy for designing these algorithms was to generate an ensemble of algorithms and test them against sample inputs.
+Like many greedy algorithms, these can be sensitive to small, sometimes unspecified, choices in implementation.
+The most important strategy for designing these algorithms is to generate an ensemble of algorithms and test them against sample inputs.
 
 \vskip 6pt
-For example, there is a common moment in these algorithms where a putative test case, partially specified, is matched against a coverage tuple, which will have $n$ specified argument values for $n$-way coverage.
+For example, there is a common moment in these algorithms where a putative test case, partially specified, is matched against a coverage tuple, which will have $t$ specified argument values for $t$-way coverage.
 Given just one argument from the test case and one argument from the tuple, there are five ways they can compare.
@@
 Now that we've explored combinatorial interaction testing, let's return to place it in the context of other similar testing techniques.
-Compared to other methods for automated test case generation, combinatorial interaction testing makes fewer tests, with some wayness guarantees.
+Compared to other methods for automated test case generation, \cit makes fewer tests, with some wayness guarantees.
 
@@
 \vskip 6pt
-Property-based testing offers a specification to describe the domain of each argument, or sets of arguments, so that the test author can focus on the domain of the function instead of the exact test suite.
+Property-based testing, for instance, offers a specification to describe the domain of each argument, or sets of arguments, so that the test author can focus on the domain of the function instead of the exact test suite.
 Tools of this kind can watch for failed tests, and then they can simplify the test arguments while checking for failure, in order to find the simplest test that fails.
@@
 
+\vskip 6pt
 A lot of the strategies in Sec.~\ref{sec:how-to-use} apply to any kind of automated test case generation.
-They point to the broad applicability of automation for testing and the effectiveness of tools that offer the test author control.
+They point to the broad applicability of automation for testing and the effectiveness of tools that offer control to the test author.
 

### 2021-07-09 paper/paper.tex
once through with final edits

@@
 
-We would like to think that our unit tests of code match perceived risk, that they match the components by which we judge risk: the hazard for failure, the cost of mitigating failure, and how much a result matters.
+We would like to think that our unit tests of code match how much risk we perceived in that code, that they match the components by which we judge risk: the hazard for failure, the cost of mitigating failure, and how much a result matters.
 However, user studies of the behavior of test authors show that our choices about testing are ruled by what is convenient within a given testing framework~\cite{Wiklund2017-ms}.
@@
 The first is that you have to test a slow function, such as a large, Monte Carlo inference.
-If the function under test runs for hours or days, then selective testing can respect resource limitations.
+If the function under test runs for hours or days, then selective testing can conserve limited resources.
 
@@
 The other circumstance is when there is a large test space.
-We've been talking about a function under test, but this is a stand-in for any test we can parametrize.
+We've been talking about a function under test, but this is a stand-in for any test we can parameterize.
 Let's say we've written an application, that we've unit tested its important supporting functions, and we want to write user-level tests that look for problems from interactions among command-line arguments and choices in parameter files.
 This can be equivalent to testing a function with twenty or more arguments.
-Twenty arguments, with four possible values each, would lead to over $10^{12}$ ways to call this function.
+Twenty arguments, with four possible values each, would lead to over 10\textsuperscript{12} ways to call this function.
 
@@
 
-\section{How to Use Combinatorial Testing}\label{sec:how-to-use}
+\section{How to Use Combinatorial Interaction Testing}\label{sec:how-to-use}
 
@@
 
-While you may already know how to use \cit from the snippet in the introduction, it can help to think of automated test case generation as a set of steps, each of which has choices to make.
+While you may already know how to use \cit from the snippet in the introduction, it can help to think of combinatorial interaction testing as a set of steps, each of which has choices to make.
 \begin{enumerate}
@@
 \subsubsection{What arguments represent}
-There are two choices to make about arguments and their values. We must decide what the arguments represent and must select particular values for those arguments.
+We must decide what the arguments represent and must select particular values for those arguments.
 
@@
 It's rare that a function expects arguments that really take only a few possible values.
-We use integers, floating-point, and strings, but a function argument can be any struct.
+We use integers, floating-point, and strings, and a function argument can be any struct.
 When we specify tests for \cit, and we choose a few argument values, they are representatives of equivalence classes.
@@
 For instance, if a given function fails for \verb|arg3<2.7|, then it will fail for \verb|arg3=2| as well as \verb|arg3=2.5|, so we consider those equivalent with respect to finding faults.
-As authors of unit tests, we select argument values that represent equivalence classes for the function under test.
 You can choose them by looking at the code or by looking at a specification for the function, but it's possible to miss an equivalence class and miss the faults discovered by that equivalence class.
@@
 \vskip 6pt
-There are other creative ways to apply automatic test case generation.
+There are other creative ways to apply \cit.
 For instance, if an application reads a \csv file, we can use \cit to ensure rows of that \csv have a wide mixture of column values.
@@
 \end{lstlisting}
-For this example, if the first argument is \verb|"quick"|, then the second argument must be \verb|0.0|.
+For this example, if the first argument is \verb|"quick"|, imagine that the function under test requires the second argument to be \verb|0.0|.
 If we generate all combinations of \verb|arg1| and \verb|arg2|, then some combinations won't make sense.
@@
 It can be more convenient to tell the \cit algorithm that certain combinations are forbidden~\cite{Petke2015-ex,Grindal2006-vy}.
+Here, the \verb|forbid| function returns \verb|true| when argument values aren't allowed by the function under test.
 \begin{lstlisting}[language=Julia]
@@
 \end{lstlisting}
-For testing functions with many arguments, this is simpler to use.
+For testing functions with many arguments, this is simpler to use than rewriting the argument list.
 
@@
 Sometimes we want to begin with tests that are particular happy paths.
-These might be statistically common call signatures, or they could be pre-specified in design documents.
+These might be statistically common call signatures, or they could be pre-specified in design documents as calls that must be tested.
 Given that our goal is to minimize resource usage, we should ensure that any tuples of argument values covered in these initial calls are included in our list of covered tuples.
@@
 You decide the wayness of coverage, which is the number of arguments for which all combinations of argument values must appear.
-As shown in Tab.~\ref{tab:samplecounts}, increasing wayness increases the number of test cases.
+As shown in Table~\ref{tab:samplecounts}, increasing wayness increases the number of test cases.
 Pairwise testing has two-way coverage, but higher wayness can yield some benefit~\cite{Petke2015-ex}.
@@
 There isn't enough evidence for this connection for us to choose wayness according to code's cyclomatic complexity, and we are counseled against making coverage the goal of unit testing~\cite{Inozemtseva2014-gz}.
+That leaves the test author to testing as much as you can afford but shifting those tests towards exercising code that is more complex.
 
 \vskip 6pt
-For \cit, we address risk by ensuring more test cases include new combinations of arguments that affect the control flow of risky code.
+For \cit, that means shifting test cases towards combinations of those arguments that affect the control flow of risky code.
 The first way to increase testing of an argument is to increase the number of values for an argument by adding corner cases.
@@
     array_of_forty_parameters...;
-    wayness = Dict(3 => [[3:6], [25:30]])
+    wayness = Dict(3 => [[3,4,5,6]])
     )
 \end{lstlisting}
-Here, the third through sixth arguments will be tested with a wayness of three, as will the twenty-fifth through thirtieth.
+Here, the third through sixth arguments will be tested with a wayness of three, generating a total of 64~test cases.
 It's unclear whether mixing wayness will still yield a small set of test cases because mixed-level covering arrays don't have well-understood bounds~\cite{Cohen2003-pg}, however sample runs show it does produce fewer test cases than raising coverage on all arguments.
@@
 A two-way excursion tries changes to any two argument values in combination.
-It produces considerably more test cases than an all-pairs design.
+It produces considerably more test cases than an all-pairs design, as shown in Table~\ref{tab:samplecounts}.
 
@@
 rng = Random.MersenneTwister(9790375)
-slow_and_short = all_triples(parameters...; engine = GND(rng = rng, M = 50))
+slow_and_short = all_triples(parameters...;
+    engine = GND(rng = rng, M = 50))
 \end{lstlisting}
@@
 One solution is to create a parallel implementation of the function under test.
-It could be an earlier version of the function, using a na{\"i}ve algorithm.
+It could be an earlier version of the function using a na{\"i}ve algorithm.
 It could be a function that computes the same values using a different mathematical representation, such as using numerical integration instead of using the result of symbolic integration.
@@
 
-There are two ways to improve upon current use of combinatorial test generation.
-One is to help the tester whose testing resources are limited, by generating fewer test cases that still meet the wayness guarantee.
-The other is to make it more convenient to use combinatorial testing within the unit testing framework.
-Here, we could generate tests with so little time and memory that there is no need to cache test cases.
-Both of these improvements are limited by our need for algorithms that support the features, described in Sec.~\ref{sec:how-to-use}, that make automated test case generation practical to use.
-
-\vskip 6pt
 The \utd package expands on the implementation of two $t$-way combinatorial interaction testing algorithms.
@@
 The other is a deterministic, parameter-choosing algorithm called \textsc{ipo-g}~\cite{Lei2008-xt}.
-Thile these algorithms have different structure, we were able to add features to them using similar basic moves.
+While these algorithms have different structure, we were able to add features to them using similar basic moves.
 
@@
 Like many greedy algorithms, these can be sensitive to small, sometimes unspecified, choices in implementation.
-The most important strategy for designing these algorithms is to generate an ensemble of algorithms and test them against sample inputs.
+We found that a successful strategy for designing these algorithms is to generate an ensemble of variants and test them against sample inputs.
 
@@
 \vskip 6pt
-Random testing also generates test cases, and we know, from Arcuri et al, that these test cases increase code coverage with increasing numbers of test cases, in a predictable way~\cite{Arcuri2012-az}.
-Random testing also has the benefit that you can run it for an arbitrarily long time during acceptance testing.
+Random testing also generates test cases, and we know, from Arcuri et~al, that these test cases increase code coverage with increasing numbers of test cases in a predictable way~\cite{Arcuri2012-az}.
+Random testing has the benefit that you can run it for an arbitrarily long time during acceptance testing.
 There is also no requirement that values be completely random within the domain of arguments.
 They are almost always biased towards values that carry risk, such as empty strings or other corner cases.
-Here, a preference for combinatorial interaction testing comes from a lack of test-running resources or the ease of specifying sample argument values instead of the complete domain of the arguments.
+Here, a preference for combinatorial interaction testing comes from a lack of test-running resources or from the ease of specifying sample argument values instead of the complete domain of the arguments.
 
@@
 These give an even distribution of values within high-dimensional spaces.
-They would be excellent to, for instance, seed an optimization problem with local minima, but they aren't designed to explore the space of execution paths of code, in the way that combinatorial methods are.
+They would be excellent to, for instance, seed an optimization problem with local minima, but they aren't designed to explore the space of execution paths of code in the way that \cit is.
 
@@
 Tools of this kind can watch for failed tests, and then they can simplify the test arguments while checking for failure, in order to find the simplest test that fails.
-This is extraordinarily useful for fault-finding but, again, will use more testing resources~\cite{loscher2018automating}.
+This is extraordinarily useful for fault-finding but, again, will use more testing resources than \cit in the absence of failures~\cite{loscher2018automating}.
 
@@
 However, this kind of automation is easy to specify and run in Julia's ecosystem.
-The most difficult part of the transition is shifting from manual checks of test results to checks that work for any combination of arguments, as described in Sec.~\ref{sec:results}.
-
-\vskip 6pt
+The most difficult part of the transition to automated test case generation is shifting from manually-computed checks of test results to checks that work for any combination of arguments, as described in Sec.~\ref{sec:results}.
 A lot of the strategies in Sec.~\ref{sec:how-to-use} apply to any kind of automated test case generation.

### 2021-07-09 paper/paper.tex
changed to text superscript

@@
 5 & 8 & 32768 & 96 & 768 & 36 & 526 \\ \hline
-10 & 4 & $>10^{6}$ & 28 & 143 & 31 & 436 \\ \hline
-10 & 8 & $>10^{9}$ & 113 & 1223 & 71 & 2276 \\ \hline
-40 & 4 & $>10^{24}$ & 45 & 290 & 121 & 7141 \\ \hline
-40 & 8 & $>10^{36}$ & 166 & 2388 & 281 & 38501 \\  \hline
+10 & 4 & >10\textsuperscript{6} & 28 & 143 & 31 & 436 \\ \hline
+10 & 8 & >10\textsuperscript{9} & 113 & 1223 & 71 & 2276 \\ \hline
+40 & 4 & >10\textsuperscript{24} & 45 & 290 & 121 & 7141 \\ \hline
+40 & 8 & >10\textsuperscript{36} & 166 & 2388 & 281 & 38501 \\  \hline
 \end{tabular}

### 2021-07-15 paper/paper.tex

@@
 This would be done by adding a \verb|wayness| argument to the function call.
-
 \begin{lstlisting}[language=Julia]
@@
 \end{lstlisting}
-Here, the third through sixth arguments will be tested with a wayness of three, generating a total of 64~test cases.
-It's unclear whether mixing wayness will still yield a small set of test cases because mixed-level covering arrays don't have well-understood bounds~\cite{Cohen2003-pg}, however sample runs show it does produce fewer test cases than raising coverage on all arguments.
+Here, an all-pairs coverage of these 40~arguments would lead to 45~test cases, and an all-triples coverage would lead to 290~test cases, but we increase coverage on only the third through sixth arguments to a wayness of three, and this increases the total to 64~test cases.
+It's unclear whether mixing wayness will always yield a small set of test cases because mixed-level covering arrays don't have well-understood bounds~\cite{Cohen2003-pg}, however sample runs show it does produce fewer test cases than raising coverage on all arguments.
 
@@
 \end{lstlisting}
-The \verb|M=50| argument to the \verb|GND| generator controls the number of times it guesses each new argument of a test case before chooses an optimal value.
+The \verb|M=50| argument to the \verb|GND| generator controls the number of times it guesses each new argument of a test case before it chooses an optimal value.
 

### 2021-10-14 dev/search_index.js
build based on 07bfdab

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"man/ipog/#In-parameter-order-General","page":"IPOG","title":"In-parameter-order General","text":"","category":"section"},{"location":"man/ipog/#Overview","page":"IPOG","title":"Overview","text":"","category":"section"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"There is an in-parameter-order general (IPOG) algorithm that is published, and I've extended it to be more user-friendly. I'll describe both here.","category":"page"},{"location":"man/ipog/#The-covering-problem","page":"IPOG","title":"The covering problem","text":"","category":"section"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"A combinatorial covering set is a way to select combinations of values for testing. We assume that there are param_cnt items to select. These could be parameter values to send to a function. They could be configuration values for a large simulation. They could be combinations of hardware to test together. We can represent a selected test case as an array of integers, [2, 4, 3, 2], which represents the second selection of the first item, the first selection of the second item, and so on. A test set is a list of test cases.","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"We say that a test set has n-way covering when we can choose any n parameters and choose any possible combination of values of those parameters, and find them in some test case of the test set. We can think of the n-way combinations as their own data structure, a covering set, where we might represent it as an array that uses 0 to indicate paramters that aren't in the cover.","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"[[1, 1, 0, 0],\n [2, 1, 0, 0],\n [1, 2, 0, 0],\n [0, 1, 1, 0]\n ...\n]","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"A test set covers these tuples if every set of non-zero values in the covering set can be found in some test case of the test set.","category":"page"},{"location":"man/ipog/#IPOG","page":"IPOG","title":"IPOG","text":"","category":"section"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"Previous algorithms constructed a single, complete set of parameter values, called a test case, one at a time. This algorithm starts with a few parameters, finds a covering set for them, and then uses this as the basis to add a parameter at a time.","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"There are a few sources for this work, which I annotate here.","category":"page"},{"location":"man/ipog/","page":"IPOG","
[…]

### 2021-10-14 paper/paper.tex

@@
 Some tools introduce more structure to choosing random arguments.
-The \texttt{QuickCheck} and \texttt{Hypothesis} packages use customized generators to create streams of test cases~\cite{loscher2018automating}.
+The \href{https://hackage.haskell.org/package/QuickCheck}{\texttt{QuickCheck}}(Haskell) and \href{https://github.com/HypothesisWorks/hypothesis}{\texttt{Hypothesis}} (Python) packages use customized generators to create streams of test cases~\cite{loscher2018automating}.
 Concolic testing records the execution of the function under test in order to generate subsequent test cases that are likely to increase line coverage~\cite{King1976-jt,Wang2018-xh,vira2019}.

### 2021-10-14 dev/search_index.js
build based on 767726f

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"man/ipog/#In-parameter-order-General","page":"IPOG","title":"In-parameter-order General","text":"","category":"section"},{"location":"man/ipog/#Overview","page":"IPOG","title":"Overview","text":"","category":"section"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"There is an in-parameter-order general (IPOG) algorithm that is published, and I've extended it to be more user-friendly. I'll describe both here.","category":"page"},{"location":"man/ipog/#The-covering-problem","page":"IPOG","title":"The covering problem","text":"","category":"section"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"A combinatorial covering set is a way to select combinations of values for testing. We assume that there are param_cnt items to select. These could be parameter values to send to a function. They could be configuration values for a large simulation. They could be combinations of hardware to test together. We can represent a selected test case as an array of integers, [2, 4, 3, 2], which represents the second selection of the first item, the first selection of the second item, and so on. A test set is a list of test cases.","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"We say that a test set has n-way covering when we can choose any n parameters and choose any possible combination of values of those parameters, and find them in some test case of the test set. We can think of the n-way combinations as their own data structure, a covering set, where we might represent it as an array that uses 0 to indicate paramters that aren't in the cover.","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"[[1, 1, 0, 0],\n [2, 1, 0, 0],\n [1, 2, 0, 0],\n [0, 1, 1, 0]\n ...\n]","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"A test set covers these tuples if every set of non-zero values in the covering set can be found in some test case of the test set.","category":"page"},{"location":"man/ipog/#IPOG","page":"IPOG","title":"IPOG","text":"","category":"section"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"Previous algorithms constructed a single, complete set of parameter values, called a test case, one at a time. This algorithm starts with a few parameters, finds a covering set for them, and then uses this as the basis to add a parameter at a time.","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"There are a few sources for this work, which I annotate here.","category":"page"},{"location":"man/ipog/","page":"IPOG","
[…]

### 2021-10-19 paper/paper.tex
in the introduction, clarified that I assume you're doing software engineering for testability and that I don't want to talk about that here

@@
 The first unit tests for a new library often derive from mimicking how a user might write client code.
-These happy-path tests are narrative.
-We may add tests for corner cases of a function under test, but these are limited by imagination and available effort.
+These happy-path tests are narrative because they tell stories of successful use.
+As we develop, we strengthen tests where we see risk in code.
+For low-level code, this may mean testing corner cases.
+For high-level code, it may mean modifying the code to be easier to test~\cite{chowdhary2009practicing}.
+Once we've done this software engineering, we can ask what tools within our testing framework can help improve test quality.
 
 \vskip 6pt
-Automated testing tools aid that effort.
-Some measure the quality of existing tests.
+Some automated testing tools measure the quality of existing tests.
 Others select which tests to run depending on test coverage or recent code modifications.

### 2021-10-19 paper/paper.tex
made clearer a claim I thought could be taken the wrong way

@@
 They are almost always biased towards values that carry risk, such as empty strings or other corner cases.
-Here, a preference for combinatorial interaction testing comes from a lack of test-running resources or from the ease of specifying sample argument values instead of the complete domain of the arguments.
+Combinatorial interaction testing is preferable to random testing when there are few test-running resources.
 

### 2021-10-20 paper/paper.tex
tests are only as good as argument values you choose

@@
 You can choose them by looking at the code or by looking at a specification for the function, but it's possible to miss an equivalence class and miss the faults discovered by that equivalence class.
+
+\vskip 6pt
+A weakness of \cit is that your tests are only as good as the argument values you choose.
+Even if you choose argument values such that some combination of them would find a failure, it's possible that the subset of test cases generated by the \cit might not include that combination.
+There is no guarantee that using automated testing to generate hundreds of tests will find a problem.
 

### 2021-10-20 paper/paper.tex
added a paragraph at the end to say large test case counts are deceiving

@@
 
+\vskip 6pt
+All of these approaches to automated test generation create more tests with less code than manual alternatives.
+This makes a test suite less brittle as the code-under-test is modified.
+It can also create test suites with a reassuring number of test cases, but none of the automated techniques above remove risk.
+We still need to rely on software engineering techniques, such as tracking of historical bug report rates, in order to understand the maturity of a code base.
+
 \section{Conclusion}
@@
 A lot of the strategies in Sec.~\ref{sec:how-to-use} apply to any kind of automated test case generation.
-They point to the broad applicability of automation for testing and the effectiveness of tools that offer control to the test author.
+They point to the broad applicability of automation for testing and to the effectiveness of tools that offer control to the test author.
 

### 2021-11-06 paper/paper.tex

@@
 In this article, we describe when to use \cit and how to use \cit within the Julia language's unit testing ecosystem.
+We introduce the \verb!UnitTestDesign.jl!
+library which has several features that make it convenient to use.
+\begin{itemize}
+    \item Different levels of coverage, including all-pairs, all-triples, and higher level coverage.
+    \item Both deterministic and stochastic generators of test cases.
+    \item An option to prime the generation of test cases with a manually-chosen list.
+    \item The ability to forbid combinations of arguments.
+\end{itemize}
 
 \vskip 6pt
-\cit is one of a few common strategies for automated test case generation.
+\cit is a popular tool for testing frameworks~\cite{pairwise-website} and one of a few common strategies for automated test case generation.
 A randomized strategy chooses argument values from the space of allowed arguments, usually with some bias towards choosing possible corner cases~\cite{Lampropoulos2020-sd,Arcuri2012-az}.

### 2021-11-06 dev/search_index.js
build based on c0617d6

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"man/ipog/#In-parameter-order-General","page":"IPOG","title":"In-parameter-order General","text":"","category":"section"},{"location":"man/ipog/#Overview","page":"IPOG","title":"Overview","text":"","category":"section"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"There is an in-parameter-order general (IPOG) algorithm that is published, and I've extended it to be more user-friendly. I'll describe both here.","category":"page"},{"location":"man/ipog/#The-covering-problem","page":"IPOG","title":"The covering problem","text":"","category":"section"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"A combinatorial covering set is a way to select combinations of values for testing. We assume that there are param_cnt items to select. These could be parameter values to send to a function. They could be configuration values for a large simulation. They could be combinations of hardware to test together. We can represent a selected test case as an array of integers, [2, 4, 3, 2], which represents the second selection of the first item, the first selection of the second item, and so on. A test set is a list of test cases.","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"We say that a test set has n-way covering when we can choose any n parameters and choose any possible combination of values of those parameters, and find them in some test case of the test set. We can think of the n-way combinations as their own data structure, a covering set, where we might represent it as an array that uses 0 to indicate paramters that aren't in the cover.","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"[[1, 1, 0, 0],\n [2, 1, 0, 0],\n [1, 2, 0, 0],\n [0, 1, 1, 0]\n ...\n]","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"A test set covers these tuples if every set of non-zero values in the covering set can be found in some test case of the test set.","category":"page"},{"location":"man/ipog/#IPOG","page":"IPOG","title":"IPOG","text":"","category":"section"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"Previous algorithms constructed a single, complete set of parameter values, called a test case, one at a time. This algorithm starts with a few parameters, finds a covering set for them, and then uses this as the basis to add a parameter at a time.","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"There are a few sources for this work, which I annotate here.","category":"page"},{"location":"man/ipog/","page":"IPOG","
[…]

### 2021-11-06 dev/search_index.js
build based on 9bc867d

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"contributing/#Contributing","page":"Contributing","title":"Contributing","text":"","category":"section"},{"location":"contributing/#Examples-of-contributions","page":"Contributing","title":"Examples of contributions","text":"","category":"section"},{"location":"contributing/","page":"Contributing","title":"Contributing","text":"Adding an algorithm for test case generation.\nTelling me which package already has an algorithm to use.\nImproving the documentation or testing builds.\nSuggesting a better API.","category":"page"},{"location":"contributing/","page":"Contributing","title":"Contributing","text":"The Github site has an Issues page, and my email is listed.","category":"page"},{"location":"contributing/#Branch-process","page":"Contributing","title":"Branch process","text":"","category":"section"},{"location":"contributing/","page":"Contributing","title":"Contributing","text":"The trunk is called main. I use PRs from branches or other repos to main. If this project needs more than that, let's discuss it.","category":"page"},{"location":"contributing/#Conduct","page":"Contributing","title":"Conduct","text":"","category":"section"},{"location":"contributing/","page":"Contributing","title":"Contributing","text":"Let's follow the Contributor Covenant Code of Conduct.","category":"page"},{"location":"man/guide/#Guide","page":"Guide","title":"Guide","text":"","category":"section"},{"location":"man/guide/#Kinds-of-test-generation","page":"Guide","title":"Kinds of test generation","text":"","category":"section"},{"location":"man/guide/","page":"Guide","title":"Guide","text":"Combinatorial coverage - Makes the shortest test sets to cover all options.\nall_values: Every value is used at least once.\nall_pairs: Every pair of values is used at least once.\nall_triples: Every triple of values is used at least once.\nall_tuples: Generate test sets with arbitrary coverage level.\nExcursions from a single parameter set\nvalues_excursion: Tries each parameter, one at a time.\npairs_excursion: Tries pairs of parameters, two at a time.\ntriples_excursion: Tries three parameters away from the original set.\nall_tuples: This function works for general excursions, too.\nFull factorial - Every combinations of parameters.\nfull_factorial: Generates all combinations of parameters, filtering those that aren't permitted.","category":"page"},{"location":"man/guide/#Same-interface-for-all-test-generators","page":"Guide","title":"Same interface for all test generators","text":"","ca
[…]

### 2021-11-06 dev/search_index.js
build based on 69dd3b0

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"man/ipog/#In-parameter-order-General","page":"IPOG","title":"In-parameter-order General","text":"","category":"section"},{"location":"man/ipog/#Overview","page":"IPOG","title":"Overview","text":"","category":"section"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"There is an in-parameter-order general (IPOG) algorithm that is published, and I've extended it to be more user-friendly. I'll describe both here.","category":"page"},{"location":"man/ipog/#The-covering-problem","page":"IPOG","title":"The covering problem","text":"","category":"section"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"A combinatorial covering set is a way to select combinations of values for testing. We assume that there are param_cnt items to select. These could be parameter values to send to a function. They could be configuration values for a large simulation. They could be combinations of hardware to test together. We can represent a selected test case as an array of integers, [2, 4, 3, 2], which represents the second selection of the first item, the first selection of the second item, and so on. A test set is a list of test cases.","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"We say that a test set has n-way covering when we can choose any n parameters and choose any possible combination of values of those parameters, and find them in some test case of the test set. We can think of the n-way combinations as their own data structure, a covering set, where we might represent it as an array that uses 0 to indicate paramters that aren't in the cover.","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"[[1, 1, 0, 0],\n [2, 1, 0, 0],\n [1, 2, 0, 0],\n [0, 1, 1, 0]\n ...\n]","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"A test set covers these tuples if every set of non-zero values in the covering set can be found in some test case of the test set.","category":"page"},{"location":"man/ipog/#IPOG","page":"IPOG","title":"IPOG","text":"","category":"section"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"Previous algorithms constructed a single, complete set of parameter values, called a test case, one at a time. This algorithm starts with a few parameters, finds a covering set for them, and then uses this as the basis to add a parameter at a time.","category":"page"},{"location":"man/ipog/","page":"IPOG","title":"IPOG","text":"There are a few sources for this work, which I annotate here.","category":"page"},{"location":"man/ipog/","page":"IPOG","
[…]
